---
title: "Fig6"
author: "Zhihao Zhu(朱志豪), Yong-Xin Liu(刘永鑫 )"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    theme: cerulean
    highlight: haddock
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: yes
    code_fold: show
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(collapse = T,  comment="#>", echo=T, message=F, warning=F)
```

## Fig.6a. Genome_diff
Three-way differential analysis comparing A. ihumii with other Alistipes species, the phylum Bacteroidota, and strains from CGBB 

```{r Fig.6a}
library(pacman)
library(ggplot2)
library(ggalluvial)
library(patchwork)
library(dplyr)
library(readxl)

df <- read_excel("Data/a_genome_diff.xlsx")

plot_data <- df %>%
  arrange(desc(GRatio)) %>% 
  mutate(
    logP = -log10(ifelse(P_value == 0, min(P_value[P_value > 0]), P_value)),
    Description = factor(Description, levels = Description),
    GeneID = factor(GeneID, levels = unique(GeneID))
  )

npg_cols <- c("#E64B35", "#4DBBD5", "#00A087", "#3C5488", "#F39B7F", 
              "#8491B0", "#91D1C2", "#B09C85", "#BC3C29", "#0072B5")

p1 <- ggplot(plot_data, aes(y = 1, axis1 = GeneID, axis2 = Description)) +
  geom_alluvium(aes(fill = GeneID, group = Description), 
                width = 0.1, alpha = 0.5, knot.pos = 0.4) +
  geom_stratum(aes(fill = GeneID), width = 0.1, color = "white", size = 0.5) +
  geom_text(stat = "stratum", aes(label = after_stat(stratum)), 
            size = 3.8, hjust = 1, nudge_x = -0.08, fontface = "plain") +
  scale_fill_manual(values = npg_cols) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_discrete(expand = expansion(mult = c(0.5, 0))) +
  coord_cartesian(clip = 'off') +
  theme_void() +
  theme(
    legend.position = "none",
    plot.margin = margin(t = 10, r = 0, b = 0, l = 20)
  )

p2 <- ggplot(plot_data, aes(x = GRatio, y = Description)) +
  geom_point(aes(size = Count, color = logP)) +
  scale_color_gradientn(colors = c("#313695", "#74add1", "#ffffbf", "#f46d43", "#a50026"), 
                        name = expression(-log[10](P))) +
  scale_size_continuous(range = c(2, 8), name = "Gene Count") +
  scale_x_continuous(expand = expansion(mult = c(0.05, 0.1))) +
  scale_y_discrete(limits = rev(levels(plot_data$Description)), expand = c(0, 0.4)) +
  labs(x = "Enrichment Ratio (GRatio)", y = NULL) +
  theme_bw() + 
  theme(
    panel.grid = element_blank(),
    panel.border = element_rect(linewidth = 0.8, fill = NA),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 10, face = "bold"),
    plot.margin = margin(t = 10, r = 5, b = 10, l = 5)
  )

final_plot <- p1 + p2 + plot_layout(widths = c(3, 1))

ggsave("Fig.6a.pdf", plot = final_plot, width = 10, height = 6, device = cairo_pdf)
```

```{r}
# load Fig.6a
knitr::include_graphics("./Figures/Fig.6a.pdf")
```

## Fig.6b. Key metabolic enzyme genes in the flavonoid degradation pathway within the Bacteroidota pangenome

```{r Fig.6b}

library(tidyverse)
library(pheatmap)

df <- readr::read_csv("Data/b_pangenome.csv")
gene_order <- c("ramA", "bglX", "Flr", "Fcr", "phy", "Chi")

presence_data <- df %>%
  filter(mapping_status == "mapped") %>%
  group_by(species, target_gene) %>%
  slice_max(bitscore, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(presence_value = case_when(
    gene_category == "core" ~ 2,
    gene_category == "accessory" ~ 1,
    TRUE ~ 0
  )) %>%
  select(species, target_gene, presence_value)

heatmap_mat <- expand_grid(
  species = unique(df$species),
  target_gene = gene_order
) %>%
  left_join(presence_data, by = c("species", "target_gene")) %>%
  mutate(presence_value = replace_na(presence_value, 0)) %>%
  pivot_wider(
    id_cols = species,
    names_from = target_gene,
    values_from = presence_value,
    values_fill = 0
  ) %>%
  column_to_rownames("species") %>%
  select(all_of(gene_order)) %>%
  as.matrix()

pdf_height <- max(6, nrow(heatmap_mat) * 0.2)

pheatmap(
  heatmap_mat,
  filename = "fig6b.pdf",
  width = 10,
  height = pdf_height,
  color = c("white", "#6BAED6", "#D73027"),
  breaks = c(-0.5, 0.5, 1.5, 2.5),
  cluster_rows = TRUE,
  cluster_cols = FALSE,
  show_rownames = TRUE,
  show_colnames = TRUE,
  fontsize = 10,
  fontsize_row = 9,
  fontsize_col = 10,
  fontface_row = "italic",
  cellwidth = 18,
  cellheight = 13,
  angle_col = 45,
  legend = TRUE,
  legend_breaks = c(0, 1, 2),
  legend_labels = c(" ", "Accessory", "Core"),
  border_color = "grey60"
)
```

```{r}
# load Fig.6b
knitr::include_graphics("./Figures/Fig.6b.pdf")
```

## Fig.6c. Differential metabolites of targeted flavonoid metabolomics
Volcano plot of differential metabolites from targeted flavonoid metabolomics of A. ihumii SX-C120 and SX-G294. The size of dots showed the VIP value

```{r Fig.6c}
library(tidyverse)
library(readxl)
library(ggrepel)

theme_set(theme_classic(base_size = 14))

overview_file <- "Data/c_metabolism.xlsx"

data <- read_excel(overview_file)
id_col   <- "ID"
name_col <- "compound name"
sample_cols <- setdiff(names(data), c(id_col, name_col))

data[[id_col]] <- as.character(data[[id_col]])
data[[name_col]] <- as.character(data[[name_col]])

meta <- tibble(Sample = sample_cols) %>%
  mutate(Group = sub("_(.*)$", "", Sample)) %>%
  filter(Group %in% c("GAM", "Y120", "Y294"))
samples_keep <- meta$Sample

abundance <- data %>% select(all_of(samples_keep)) %>% as.matrix()
rownames(abundance) <- make.unique(data[[id_col]])

metabolite_anno <- data %>% select(ID = !!id_col, Name = !!name_col) %>%
  mutate(ID = make.unique(ID))

abund_t <- t(abundance)
if (any(is.na(abund_t)) || any(abund_t == 0)) {
  min_pos <- min(abund_t[abund_t > 0], na.rm = TRUE)
  abund_t[is.na(abund_t)] <- min_pos / 2
  abund_t[abund_t == 0]   <- min_pos / 2
}
log2_abund <- log2(abund_t)
stopifnot(all(rownames(log2_abund) == meta$Sample))

diff_test <- function(g1, g2) {
  s1 <- meta %>% filter(Group == g1) %>% pull(Sample)
  s2 <- meta %>% filter(Group == g2) %>% pull(Sample)
  m1 <- log2_abund[rownames(log2_abund) %in% s1, , drop = FALSE]
  m2 <- log2_abund[rownames(log2_abund) %in% s2, , drop = FALSE]
  res <- lapply(seq_len(ncol(log2_abund)), function(j) {
    p <- tryCatch(t.test(m1[, j], m2[, j])$p.value, error = function(e) NA)
    data.frame(ID = colnames(log2_abund)[j],
               log2FC = mean(m1[, j], na.rm = TRUE) - mean(m2[, j], na.rm = TRUE),
               pvalue = p)
  }) %>% bind_rows() %>%
    mutate(FDR = p.adjust(pvalue, method = "BH"),
           FDR = ifelse(is.na(FDR) | FDR == 0, 1e-300, FDR),
           negLog10FDR = -log10(FDR)) %>%
    left_join(metabolite_anno, by = "ID") %>%
    mutate(Metabolite = ifelse(is.na(Name) | Name == "", ID, Name))
  return(res)
}

res <- diff_test("Y120", "Y294")

volc_data <- res %>%
  mutate(Regulation = case_when(
    log2FC > 0  ~ "Up in Y120",
    log2FC < 0  ~ "Up in Y294",
    TRUE        ~ "No change"
  )) %>%
  mutate(Regulation = factor(Regulation, levels = c("Up in Y120", "Up in Y294", "No change")))

label_df <- volc_data %>% arrange(desc(abs(log2FC))) %>% slice_head(n = 20)

max_abs <- max(abs(volc_data$log2FC), na.rm = TRUE)

p_volcano <- ggplot(volc_data, aes(x = log2FC, y = negLog10FDR, color = Regulation)) +
  geom_point(alpha = 0.8, size = 4) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50", linewidth = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50", linewidth = 0.5) +
  scale_color_manual(values = c("Up in Y120" = "#D73027", "Up in Y294" = "#4575B4",
                                "No change" = "grey70")) +
  geom_text_repel(data = label_df, aes(label = Metabolite), size = 3,
                  max.overlaps = 100, box.padding = 0.3, point.padding = 0.2,
                  segment.color = "grey50") +
  labs(x = "log2(Fold Change) (Y120 / Y294)",
       y = expression(-log[10]("FDR")),
       title = "Volcano plot: Y120 vs Y294") +

  scale_x_continuous(
    limits = c(-max_abs, max_abs),
    breaks = seq(floor(-max_abs), ceiling(max_abs), by = 1)
  ) +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    panel.border = element_rect(linewidth = 0.8, fill = NA),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    legend.title = element_blank(),
    legend.text = element_text(size = 11),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(color = "black", size = 11)
  )

ggsave("Fig6c.pdf", p_volcano, width = 8, height = 6, dpi = 600)
```

```{r}
# load Fig.6c
knitr::include_graphics("./Figures/Fig.6c.pdf")
```

## Fig.6d. Differential metabolites of targeted flavonoid metabolomics
Differences in  taxifolin concentrations after 96 hours of culture with A.ihumii SX-C120, determined by targeted flavonoid metabolomics. Ctrl(medium) represents blank medium without strain supplementation as the control group. Each line links paired identical biological replicates between the Ctrl(medium) and SX-C120 treatment groups.

```{r}
# load Fig.6d
knitr::include_graphics("./Figures/Fig.6d.pdf")
```

## Fig.6e. Quantification of taxifolin levels in mice feces
Fecal levels were determined by ELISA (n = 5).

```{r Fig.6e}
library(tidyverse)
library(readxl)
library(emmeans)
library(ggsignif)

my_theme <- theme_bw() +
  theme(
    panel.grid = element_blank(),
    panel.border = element_blank(),         
    axis.line = element_line(color = "black", linewidth = 0.8), 
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    legend.position = "none",
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(color = "black", size = 11),
    plot.margin = unit(c(0.8, 0.8, 0.8, 0.8), "cm")
  )

group_colors <- c(
  "SAMR1"       = "#BFBEBE",
  "SAMP8"       = "#00B335",
  "SX-C120 CFS" = "#E74C3C",
  "SX-C120 LBC" = "#4287f5"
)

file_path <- "Data/e_taxifolin.csv"
df_raw <- read_csv(file_path)

colnames(df_raw)[1] <- "SampleID"

df_long <- df_raw %>%
  pivot_longer(
    cols = -SampleID,
    names_to = "Group",
    values_to = "Value"
  ) %>%
  filter(Group %in% names(group_colors)) %>%
  mutate(
    Group = factor(Group, levels = names(group_colors)),
    Value = Value / 1000  
  )

fit <- aov(Value ~ Group, data = df_long)
emm <- emmeans(fit, ~ Group)
dunnett_res <- contrast(emm, method = "dunnett", ref = "SAMP8") %>% as_tibble()

p2star <- function(p){
  case_when(
    p <= 0.001 ~ "***",
    p <= 0.01  ~ "**",
    p <= 0.05  ~ "*",
    TRUE       ~ "ns"
  )
}

star1 <- p2star(dunnett_res$p.value[1]) 
star2 <- p2star(dunnett_res$p.value[2]) 
star3 <- p2star(dunnett_res$p.value[3]) 

pos1 <- 11.0
pos2 <- 12.5
pos3 <- 14.0

p_box <- ggplot(df_long, aes(x = Group, y = Value)) +
  geom_boxplot(aes(color = Group, fill = Group),
               alpha = 0.5, width = 0.6, outlier.shape = NA, linewidth = 0.8, fatten = 1.5) +
  geom_jitter(aes(fill = Group), width = 0.12, size = 3.5, alpha = 0.8, 
              shape = 21, color = "black", stroke = 0.5) +
  scale_color_manual(values = group_colors) +
  scale_fill_manual(values = group_colors) +
  geom_signif(comparisons = list(c("SAMR1", "SAMP8")), 
              annotations = star1, y_position = pos1, tip_length = 0.02, textsize = 4.5) +
  geom_signif(comparisons = list(c("SAMP8", "SX-C120 CFS")), 
              annotations = star2, y_position = pos2, tip_length = 0.02, textsize = 4.5) +
  geom_signif(comparisons = list(c("SAMP8", "SX-C120 LBC")), 
              annotations = star3, y_position = pos3, tip_length = 0.02, textsize = 4.5) +
  
  labs(x = NULL, y = "Taxifolin (ng/mL)", title = "Taxifolin Concentration") +
  scale_y_continuous(
    limits = c(0, 15.5),              
    breaks = seq(0, 10, by = 2),      
    expand = expansion(mult = c(0, 0)) 
  ) +
  my_theme

ggsave("Fig6e.pdf", plot = p_box, width = 5, height = 6, dpi = 600)
```

```{r}
# load Fig.6e
knitr::include_graphics("./Figures/Fig.6e.pdf")

# The subsequent drawing of the box line diagram has been modified accordingly on this script
```

## Fig.6f. Genomic context of the Flr-like sequence


```{r}
library(ggplot2)
library(dplyr)
library(readr)
library(stringr)

neighbor_file <- "Data/f_neighborhood_10kb.csv"
annotation_file <- "Data/f_neighbor_annotation.emapper.annotations"

target_id <- "1_1283"

out_prefix <- "Fig.6f"


neighbor <- read_csv(neighbor_file, show_col_types = FALSE)

required_cols <- c("gene_id", "start", "end", "strand", "length_bp", "distance_to_target_bp")
missing_cols <- setdiff(required_cols, colnames(neighbor))

if (length(missing_cols) > 0) {
  stop("Missing columns in neighborhood file: ", paste(missing_cols, collapse = ", "))
}

read_eggnog <- function(file) {
  lines <- readLines(file)
  lines2 <- lines[!grepl("^##", lines)]
  header_idx <- grep("^#query\\t|^#query\\b", lines2)
  if (length(header_idx) == 0) {
    stop("Cannot find eggNOG header line starting with #query.")
  }
  
  lines2 <- lines2[header_idx[1]:length(lines2)]
  tmp <- tempfile(fileext = ".tsv")
  writeLines(lines2, tmp)
  anno <- read.delim(
    tmp,
    header = TRUE,
    sep = "\t",
    quote = "",
    comment.char = "",
    check.names = FALSE,
    fill = TRUE,
    stringsAsFactors = FALSE
  )
  colnames(anno)[colnames(anno) == "#query"] <- "query"
  return(anno)
}

anno <- read_eggnog(annotation_file)

cat("eggNOG annotation columns:\n")
print(colnames(anno))

if (!"query" %in% colnames(anno)) {
  stop("Column 'query' not found after reading eggNOG file.")
}

if (!"Description" %in% colnames(anno)) {
  warning("Column 'Description' not found. Creating empty Description column.")
  anno$Description <- NA
}

if (!"PFAMs" %in% colnames(anno)) {
  warning("Column 'PFAMs' not found. Creating empty PFAMs column.")
  anno$PFAMs <- NA
}

anno_simple <- anno %>%
  dplyr::select(
    gene_id = query,
    COG_category,
    description = Description,
    PFAMs
  )

neighbor2 <- neighbor %>%
  dplyr::left_join(anno_simple, by = "gene_id")

neighbor2$description[is.na(neighbor2$description)] <- "No eggNOG annotation"
neighbor2$PFAMs[is.na(neighbor2$PFAMs)] <- ""

neighbor2$annot_text <- paste(
  neighbor2$description,
  neighbor2$PFAMs,
  sep = " "
)

neighbor2$annot_text_lower <- tolower(neighbor2$annot_text)

neighbor2$category <- "Other"

neighbor2$category[neighbor2$gene_id == target_id] <- "Target flr-like"

neighbor2$category[
  neighbor2$category != "Target flr-like" &
    str_detect(neighbor2$annot_text_lower, "integrase|phage_integrase|phage integrase")
] <- "Integrase"

neighbor2$category[
  neighbor2$category != "Target flr-like" &
    str_detect(neighbor2$annot_text_lower, "transpos|insertion sequence|is21|istb|dde")
] <- "Transposase / IS"

neighbor2$category[
  neighbor2$category != "Target flr-like" &
    str_detect(neighbor2$annot_text_lower, "relaxase")
] <- "Relaxase"

neighbor2$category[
  neighbor2$category != "Target flr-like" &
    str_detect(neighbor2$annot_text_lower, "mobilisation|mobilization|mobc|\\bmob\\b")
] <- "Mobilization"

neighbor2$category[
  neighbor2$category != "Target flr-like" &
    str_detect(neighbor2$annot_text_lower, "hth|arac|transcriptional regulator")
] <- "Regulator"

neighbor2$category[
  neighbor2$category != "Target flr-like" &
    str_detect(neighbor2$annot_text_lower,
               "fmn|flavin|flavodoxin|reductase|amidohydrolase|tautomerase|cupin|aldo|keto")
] <- "Metabolic / redox"

neighbor2$label <- neighbor2$gene_id

neighbor2$label[neighbor2$category == "Integrase"] <- "integrase"
neighbor2$label[neighbor2$category == "Transposase / IS"] <- "IS21/IstB"
neighbor2$label[neighbor2$category == "Relaxase"] <- "relaxase"
neighbor2$label[neighbor2$category == "Mobilization"] <- "MobC"
neighbor2$label[neighbor2$category == "Regulator"] <- "regulator"
neighbor2$label[neighbor2$category == "Metabolic / redox"] <- "metabolic"
neighbor2$label[neighbor2$category == "Target flr-like"] <- "flr-like\n1_1283"

target_row <- neighbor2 %>% dplyr::filter(gene_id == target_id)

if (nrow(target_row) == 0) {
  stop("Target gene not found in neighbor table: ", target_id)
}

target_center <- (target_row$start + target_row$end) / 2

neighbor2 <- neighbor2 %>%
  dplyr::mutate(
    rel_start_kb = (start - target_center) / 1000,
    rel_end_kb   = (end   - target_center) / 1000,
    rel_mid_kb   = (rel_start_kb + rel_end_kb) / 2
  ) %>%
  dplyr::arrange(rel_start_kb)

make_arrow_polygon <- function(xmin, xmax, strand, gene_id,
                               y = 0,
                               height = 0.38,
                               head_len = 0.18) {
  
  len <- abs(xmax - xmin)
  hl <- min(head_len, len * 0.45)
  y_bottom <- y - height / 2
  y_top    <- y + height / 2
  
  if (strand == "+") {
    x <- c(xmin, xmax - hl, xmax, xmax - hl, xmin)
    yv <- c(y_bottom, y_bottom, y, y_top, y_top)
  } else {
    x <- c(xmax, xmin + hl, xmin, xmin + hl, xmax)
    yv <- c(y_bottom, y_bottom, y, y_top, y_top)
  }
  data.frame(
    gene_id = gene_id,
    x = x,
    y = yv,
    stringsAsFactors = FALSE
  )
}

poly_df <- do.call(
  rbind,
  lapply(seq_len(nrow(neighbor2)), function(i) {
    make_arrow_polygon(
      xmin = neighbor2$rel_start_kb[i],
      xmax = neighbor2$rel_end_kb[i],
      strand = neighbor2$strand[i],
      gene_id = neighbor2$gene_id[i]
    )
  })
)

poly_df <- poly_df %>%
  dplyr::left_join(
    neighbor2 %>% dplyr::select(gene_id, category),
    by = "gene_id"
  )

color_map <- c(
  "Integrase" = "#D73027",
  "Transposase / IS" = "#FC8D59",
  "Relaxase" = "#F46D43",
  "Mobilization" = "#FDAE61",
  "Regulator" = "#ABDDA4",
  "Metabolic / redox" = "#74ADD1",
  "Target flr-like" = "#313695",
  "Other" = "grey75"
)

mge_categories <- c("Integrase", "Transposase / IS", "Relaxase", "Mobilization")

mge_genes <- neighbor2 %>%
  dplyr::filter(category %in% mge_categories)

if (nrow(mge_genes) > 0) {
  mge_xmin <- min(mge_genes$rel_start_kb)
  mge_xmax <- max(mge_genes$rel_end_kb)
} else {
  mge_xmin <- NA
  mge_xmax <- NA
}

metabolic_genes <- neighbor2 %>%
  dplyr::filter(category %in% c("Target flr-like", "Metabolic / redox"))

if (nrow(metabolic_genes) > 0) {
  meta_xmin <- min(metabolic_genes$rel_start_kb)
  meta_xmax <- max(metabolic_genes$rel_end_kb)
} else {
  meta_xmin <- NA
  meta_xmax <- NA
}

p <- ggplot()

if (!is.na(mge_xmin)) {
  p <- p +
    annotate(
      "rect",
      xmin = mge_xmin,
      xmax = mge_xmax,
      ymin = -0.45,
      ymax = 0.55,
      fill = "#FEE0D2",
      alpha = 0.45
    ) +
    annotate(
      "text",
      x = (mge_xmin + mge_xmax) / 2,
      y = 0.72,
      label = "mobility module",
      size = 4,
      color = "#A50F15",
      fontface = "bold"
    )
}

if (!is.na(meta_xmin)) {
  p <- p +
    annotate(
      "rect",
      xmin = meta_xmin,
      xmax = meta_xmax,
      ymin = -0.45,
      ymax = 0.55,
      fill = "#DEEBF7",
      alpha = 0.35
    ) +
    annotate(
      "text",
      x = (meta_xmin + meta_xmax) / 2,
      y = -0.72,
      label = "flr-like / redox-associated module",
      size = 4,
      color = "#08519C",
      fontface = "bold"
    )
}

p <- p +
  geom_polygon(
    data = poly_df,
    aes(x = x, y = y, group = gene_id, fill = category),
    color = "black",
    linewidth = 0.35
  ) +
  geom_text(
    data = neighbor2,
    aes(x = rel_mid_kb, y = 0.38, label = label),
    size = 3.2,
    angle = 45,
    hjust = 0,
    vjust = 0
  ) +
  geom_vline(
    xintercept = 0,
    linetype = "dashed",
    color = "#313695",
    linewidth = 0.6
  ) +
  scale_fill_manual(values = color_map, drop = FALSE) +
  scale_x_continuous(
    breaks = seq(
      floor(min(neighbor2$rel_start_kb)),
      ceiling(max(neighbor2$rel_end_kb)),
      by = 2
    )
  ) +
  coord_cartesian(
    ylim = c(-0.95, 1.15),
    expand = FALSE
  ) +
  theme_classic(base_size = 14) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.line.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  labs(
    title = "Genomic context of SX_C120_1283 flr-like",
    subtitle = "flr-like is embedded in a mobility-associated genomic region",
    x = "Position relative to SX_C120_1283 center (kb)",
    y = ""
  )

pdf_file <- paste0(out_prefix, ".pdf")

if (capabilities("cairo")) {
  ggsave(
    filename = pdf_file,
    plot = p,
    width = 13,
    height = 4,
    device = cairo_pdf
  )
} else {
  ggsave(
    filename = pdf_file,
    plot = p,
    width = 13,
    height = 4
  )
}
```

```{r Fig.6f}
# load Fig.6f
knitr::include_graphics("./Figures/Fig.6f.pdf")
```

## Fig.6g. Molecular docking simulation of Flr-like protein with quercetin
Molecular docking simulation of Flr-like protein with quercetin. Magnified view shows the binding pocket and key binding sites. This figure was generated by PyMOL.

```{r Fig.6g}
# load Fig.6g
knitr::include_graphics("./Figures/Fig.6g.pdf")
```







