---
title: "Centenarians cohort data visualization (Fig. 2)"
author: "Yuanping Zhou (周远平), Yong-Xin Liu(刘永鑫)"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    theme: cerulean
    highlight: haddock
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: yes
    code_fold: show
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = T, echo=T, comment="#>", message=F, warning=F,
	fig.align="center", fig.width=5, fig.height=3, dpi=150)
```

```{r package installation}
# This rmarkdown analysis workflow use many R packages for data analysis, so to make it work well, we first need to install all the packages related.

## package installation through cran-website by running following codes before the first time you use this workflow.
# install.packages("ggplot2")
# install.packeages("dplyr")
# install.pacakges("scales")
# install.packages("tidyverse")
# install.packages("reshape2")
# install.packages("tidyr")
# install.packages("ggrepel")
# install.packages("multcompView")
# install.packages("PMCMRplus")
# install.packages("ape")
# install.packages("vegan")
# install.packages("RColorBrewer")
# install.packages("data.table")
# install.packages("Hmisc")
# install.packages("igraph")
# install.packages("ggVennDiagram")
# install.packages("ggprism")
# install.packages("plyr")
# install.packages("ggfun")
# install.packages("cowplot")
# install.packages("magrittr")

## packages installed from Bioconductor or github websites
# install.packages("BiocManager")
# library(BiocManager)
# install("remotes")
# install("sna")
# install("tidyfst")
# install("phyloseq")
# install("ggalluvial")
# install("ggraph")
# install("WGCNA")
# install("ggnewscale")
# install("pulsar")
# install("patchwork")
# remotes::install_github("taowenmicro/EasyStat")
# remotes::install_github("taowenmicro/ggClusterNet")
# install("ALDEx2")

```

## Fig.2A. Rerafaction curve

Rarefaction curve

```{r package load}
# load related packages
library("ggplot2")
library("dplyr")
library("scales")
library("tidyverse")
library("reshape2")
library("tidyr")
```

```{r rarefaction curve}
###########################################################################################################
## Centenarians
# Load MAG (metagenome-assembed genome) table of all the samples, which was generated using the coverm in our Easy-Metagenome pipeline.
MAG_table_all <- read.table("./data_fig2/abundance.tsv", row.names= 1,  header=T, sep="\t")
dim(MAG_table_all)
# Load metadata table
metadata<- read.table("./data_fig2/metadata_rmNA.txt", header = T, sep = "\t")
rownames(metadata) <- metadata$SampleID
metadata_C <- metadata %>% filter(Group == "C") # n=108

# Select MAG_table of the centenarians based Group column of metadata
MAG_table <-MAG_table_all[, rownames(metadata_C)] # n=108

# Load the taxonomic table of MAGs
taxonomy <- read.delim("./data_fig2/drep95_tax.txt", row.names= 1,header=T, sep="\t")
# Add a new column called Full, cotaining the taxonomic information from Phylum to species, which is separated using semicomma.
taxonomy$Full <- paste(taxonomy$Phylum, taxonomy$Class, taxonomy$Order, taxonomy$Family, taxonomy$Genus, taxonomy$Species, sep = ";")

# Extract only those MAGs in both MAG_table and the taxonomic table
idx <- rownames(MAG_table) %in% rownames(taxonomy)
MAG_table <- MAG_table[idx, ]
taxonomy <- taxonomy[rownames(MAG_table), ]

# Rarefraction curve data generation
sample_rare  <-  function(df, count_cutoff = .01, length = 108, rep = 30){  
  result <- data.frame(sample = c(0), richness = c(0))
  count <- df
  # Set MAG table to binary for easy richness calculation
  count[count < count_cutoff] = 0
  count[count >= count_cutoff] = 1
  # Sample number
  n <- dim(count)[2]
  # 
  x <- unique(as.integer(seq(1, 108, length.out = 108)))
  for (i in x){
    m <- choose(n, i)
    if (m > rep){m = rep}
    # loop list and calculate richness
    for(j in 1:m) {
      idx <- sample(n, i)
      temp <- count[, idx, drop = F]
      # subset non-zero row
      temp1 <- temp[rowSums(temp)>0, , drop=F]
      # row number is accumulative MAGs
      result <- rbind(result, c(i, dim(temp1)[1]))
    }
  }
  # remove start 0,0
  result <- result[-1, ]
  # factor draw as each box
  result$sample <- factor(result$sample, levels = unique(result$sample))
  return(result)
}
rare_box <- sample_rare(MAG_table, count_cutoff = .01, length = 108, rep = 30)
rare_box$group <- "C"
rare_box_C <- rare_box
colnames(rare_box_C) <- c("Number of Samples", "Number of Species","group")
#####################################################################################################
##  Offspring
# Select the MAG table of the Lineal descendants
metadata_L <- metadata %>% filter(Group == "L") # n=61
MAG_table<- MAG_table_all[, rownames(metadata_L)] # n=61

# Taxonomy table
taxonomy <- read.delim("./data_fig2/drep95_tax.txt", row.names= 1,header=T, sep="\t")
taxonomy$Full <- paste(taxonomy$Phylum,taxonomy$Class,taxonomy$Order,taxonomy$Family,taxonomy$Genus,taxonomy$Species,sep = ";")

# Extract common samples in the two tables
idx <- rownames(MAG_table) %in% rownames(taxonomy)
MAG_table <- MAG_table[idx, ]
taxonomy <- taxonomy[rownames(MAG_table), ]

# Rarefraction curve
sample_rare  <-  function(df, count_cutoff = .01, length = 61, rep = 30){  
  result <- data.frame(sample = c(0), richness = c(0))
  count <- df
  # Set MAG table to binary for easy richness calculation
  count[count < count_cutoff] = 0
  count[count >= count_cutoff] = 1
  # Sample number
  n <- dim(count)[2]
  # 
  x <- unique(as.integer(seq(1, 61, length.out = 61)))
  for (i in x){
    m <- choose(n, i)
    if (m > rep){m = rep}
    # loop list and calculate richness
    for(j in 1:m) {
      idx <- sample(n, i)
      temp <- count[, idx, drop = F]
      # subset non-zero row
      temp1 <- temp[rowSums(temp)>0, , drop=F]
      # row number is accumulative MAGs
      result <- rbind(result, c(i, dim(temp1)[1]))
    }
  }
  # remove start 0,0
  result <- result[-1, ]
  # factor draw as each box
  result$sample <- factor(result$sample, levels = unique(result$sample))
  return(result)
}
rare_box <- sample_rare(MAG_table, count_cutoff = .01, length = 61, rep = 30)
rare_box$group <- "L"
rare_box_L<-rare_box
colnames(rare_box_L) <- c("Number of Samples", "Number of Species","group")
# View(rare_box_L)
#############################################################################################
# Elderly
# Select the MAG table of the Non-lineal elderly
metadata_E <- metadata %>% filter(Group == "E") # n=72
dim(metadata_E)
MAG_table <- MAG_table_all[, rownames(metadata_E)] # n = 72

# Taxonomy table
taxonomy <- read.delim("./data_fig2/drep95_tax.txt", row.names = 1, header = T, sep = "\t")
taxonomy$Full <- paste(taxonomy$Phylum,taxonomy$Class,taxonomy$Order,taxonomy$Family,taxonomy$Genus,taxonomy$Species, sep = ";")

# Extract only those samples in common between the two tables
idx <- rownames(MAG_table) %in% rownames(taxonomy)
MAG_table <- MAG_table[idx, ]
taxonomy <- taxonomy[rownames(MAG_table), ]

# Rarefraction curve
sample_rare  <-  function(df, count_cutoff = .01, length =72, rep = 30){  
  result <- data.frame(sample = c(0), richness = c(0))
  count <- df
  # Set MAG table to binary for easy richness calculation
  count[count < count_cutoff] = 0
  count[count >= count_cutoff] = 1
  # Sample number
  n <- dim(count)[2]
  # 
  x <- unique(as.integer(seq(1, 72, length.out = 72)))
  for (i in x){
    m <- choose(n, i)
    if (m > rep){m = rep}
    # loop list and calculate richness
    for(j in 1:m) {
      idx <- sample(n, i)
      temp <- count[, idx, drop = F]
      # subset non-zero row
      temp1 <- temp[rowSums(temp)>0, , drop=F]
      # row number is accumulative MAGs
      result <- rbind(result, c(i, dim(temp1)[1]))
    }
  }
  # remove start 0,0
  result <- result[-1,]
  # factor draw as each box
  result$sample <- factor(result$sample, levels = unique(result$sample))
  return(result)
}
rare_box <- sample_rare(MAG_table, count_cutoff = .01, length = 72, rep = 30)
rare_box$group <- "E"
rare_box_E <- rare_box
colnames(rare_box_E) <- c("Number of Samples", "Number of Species","group")
#####################################################################################################################
# Young group
# Select the MAG table of the Non-lineal Young
metadata_Y <- metadata %>% filter(Group == "Y") # n=65 volunteers
MAG_table<- MAG_table_all[, rownames(metadata_Y)] # n=65 volunteers

# Taxonomy table
taxonomy <- read.delim("./data_fig2/drep95_tax.txt", row.names = 1,header = T, sep ="\t")
taxonomy$Full <- paste(taxonomy$Phylum,taxonomy$Class,taxonomy$Order,taxonomy$Family,taxonomy$Genus,taxonomy$Species, sep = ";")

# Extract only those samples in common between the two tables
idx <- rownames(MAG_table) %in% rownames(taxonomy)
MAG_table <- MAG_table[idx, ]
taxonomy <- taxonomy[rownames(MAG_table), ]

# Rarefraction curve
sample_rare  <-  function(df, count_cutoff = .01, length =65, rep = 30){  
  result <- data.frame(sample = c(0), richness = c(0))
  count <- df
  # Set MAG table to binary for easy calculate richness
  count[count < count_cutoff] = 0
  count[count >= count_cutoff] = 1
  # Sample number
  n <- dim(count)[2]
  # 
  x <- unique(as.integer(seq(1, 65, length.out = 65)))
  for (i in x){
    m <- choose(n, i)
    if (m > rep){m = rep}
    # loop list and calculate richness
    for(j in 1:m) {
      idx <- sample(n, i)
      temp <- count[, idx, drop = F]
      # subset non-zero row
      temp1 <- temp[rowSums(temp)>0, , drop=F]
      # row number is accumulative MAGs
      result <- rbind(result, c(i, dim(temp1)[1]))
    }
  }
  # remove start 0,0
  result <- result[-1,]
  # factor draw as each box
  result$sample <- factor(result$sample, levels = unique(result$sample))
  return(result)
}
rare_box <- sample_rare(MAG_table, count_cutoff = .01, length = 65, rep = 30)
rare_box$group <- "Y"
rare_box_Y <- rare_box
colnames(rare_box_Y) <- c("Number of Samples", "Number of Species","group")
##############################
rare_box <- rbind(rare_box_C, rare_box_E, rare_box_L, rare_box_Y)
# save the data
write.table(rare_box, paste0("./data_fig2/species", "_rare_curve.txt"), sep = "\t", quote = F, col.names=T,row.names=F, na="")
#####################################
# Plot rarefaction curves
rm(list=ls())
library(ggplot2)
# Please calculate median or mean for the sampling data as "Species_rare_curve_average.txt" we provided
Rare_data <- read.table("./data_fig2/species_rare_curve.txt",sep = "\t",header = T)
# rename the column names of the rarefaction curve data
names(Rare_data) <- c("Number_of_samples","Number_of_species","Group")
Rare_data <- Rare_data %>% group_by(Group,Number_of_samples) %>% mutate(mean=round(mean(Number_of_species),digits=0)) 
  
Rare_data$Group <- factor(Rare_data$Group, levels = c("C","L","E","Y"),ordered = T)
Rare_data <- na.omit(Rare_data)
dim(Rare_data)
library(forcats)
Rare_data$Group <- fct_recode(Rare_data$Group, Centenarian = "C", Offspring = "L", Elderly = "E", Young = "Y")
# write.table(Rare_data, file = "Rarefaction_data.tsv", sep = "\t", row.names = FALSE)
library(ggrepel) # Use this package to automatically adjust the position of labels in the graph.
p <- ggplot(Rare_data, aes(x = Number_of_samples, y = mean, color = Group)) +
  geom_line(linewidth = 1, show.legend = FALSE) +
  scale_color_manual(values = c("tomato", "orange", "steelblue", "darkgreen")) +
  scale_x_continuous(limits = c(0, 120), breaks = seq(0, 120, by = 30)) +
  theme_bw() +
  ylab("Number of species") +
  theme(
    panel.grid.major = element_line(colour = NA),
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size=8),
    axis.title.y = element_text(size=8),
    axis.text.x = element_text(size=6),
    axis.text.y = element_text(size=6)
  ) +
  # 在每条线的最后一个点上标注group
  geom_text_repel(
    data = Rare_data %>% group_by(Group) %>% slice_max(Number_of_samples),
    aes(label = Group),
    show.legend = FALSE,
    nudge_x = 5,
    size = 3
  )
p
ggsave("Fig.2A.pdf", p, width = 60, height = 59, units = "mm")
```

## Fig.2B. PCoA of gut microbiome composition.

```{r beta diversity analysis}
library(ggplot2)
library(ape)
library(tidyverse)
library(multcomp)
library(extrafont)
library(patchwork)
library(vegan)
library(reshape2)
library(ggsci)
library(scales)

rm(list=ls())
set.seed(1289)
MAG_tab <- read.table("./data_fig2/mag_tab.txt",sep = "\t", header = T, row.names = 1)
MAG_table <- t(MAG_tab)
dist.df <- vegdist(MAG_table, method = "bray")

pcoa <- pcoa(dist.df, correction = "none", rn=NULL)

groups <- read.table("./data_fig2/metadata.txt",sep="\t",header=TRUE)
groups$Group[groups$Group == "C"] <- "Centenarian"
groups$Group[groups$Group == "L"] <- "Offspring"
groups$Group[groups$Group == "E"] <- "Elderly"
groups$Group[groups$Group == "Y"] <- "Young"

# View(groups)
rownames(groups)<-groups$SampleID
PC1<- pcoa$vectors[,1]
PC2<- pcoa$vectors[,2]

groups<- groups[match(rownames(pcoa$vectors),rownames(groups)),]
pcoadata<- data.frame(rownames(pcoa$vectors),PC1,PC2,groups$Group)
colnames(pcoadata)<-c("sample","PC1","PC2","group")
# View(pcoadata)
pcoadata$group %>% unique()
pcoadata$group<- factor(pcoadata$group,levels=c("Centenarian","Offspring","Elderly","Young"))
otu.adonis<- adonis2(dist.df~group, data=pcoadata, permutation = 9999)
# View(otu.adonis)
write.table(otu.adonis,"beta_bray-curtis_adonis.tsv", sep = "\t", quote = F)
#####################################################
# Boxplot
df <- pcoadata
df1 <- df %>% group_by(group) %>% summarise(Max = max(PC1))
df2 <- df %>% group_by(group) %>% summarise(Max = max(PC2))
df1$Max <- df1$Max + max(df1$Max)*0.1
df2$Max <- df2$Max + max(df2$Max)*0.1
tuk1<- aov(PC1~group, data = pcoadata) %>%
  glht(alternative = "two.sided", linfct = mcp(group = "Tukey")) %>% cld(alpha = 0.05)

tuk2 <- aov(PC2~group, data = pcoadata) %>%
  glht(alternative = "two.sided", linfct = mcp(group = "Tukey")) %>% cld(alpha = 0.05)

res <- data.frame(PC1=tuk1$mcletters$Letters, PC2 = tuk2$mcletters$Letters, df1 = df1$Max, df2 = df2$Max, group = df1$group)
res$group <- factor(res$group, levels = c("Centenarian","Offspring","Elderly","Young"))
# write.table(pcoadata, file = "pcoadata.tsv", sep = "\t", row.names = FALSE)
# write.table(res, file = "pcoa_stat.tsv", row.names =FALSE, sep = "\t" )
######################################################
p1 <- ggplot(pcoadata, aes(PC1, PC2, colour = group))+
  geom_point(aes(colour = group), size = 1)+
  labs(x = (floor(pcoa$values$Relative_eig[1]*100)) %>% paste0("PCoA1 ( ", ., "%", ")"), 
       y = (floor(pcoa$values$Relative_eig[2]*100)) %>% paste0("PCoA2 ( ", ., "%", " )")) +
  scale_colour_manual(values = c("tomato","orange","steelblue","darkgreen"))+
  stat_ellipse(aes(PC1, PC2), level = 0.95)+
  theme(text = element_text(size = 15))+
  geom_vline(aes(xintercept = 0), linetype = "dotted")+
  geom_hline(aes(yintercept = 0), linetype = "dotted")+
  theme(panel.background = element_rect(fill = "white", colour = "black"), 
        axis.title.x = element_text(colour = "black", size = 15),
        axis.title.y = element_text(colour = "black", size = 15),
        axis.text = element_text(colour = "black", size = 12),
        legend.title = element_blank(),
        legend.key.height = unit(0.4, "cm"),
        legend.position = "none",
        panel.grid = element_blank())
p1
################################################
p2 <- ggplot(pcoadata, aes(group, PC1))+
  geom_boxplot(aes(fill = group, alpha = 0.1), outlier.colour = NA)+
  scale_fill_manual(values = c("tomato","orange","steelblue","darkgreen"))+
  geom_text(data = res, aes(x = group, y = df1, label = PC1),
            size = 5, color = "black", fontface = "plain")+
  theme(panel.background = element_rect(fill = "white", colour = "black"), 
        axis.ticks.length = unit(0.4, "lines"),
        axis.ticks = element_line(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_text(colour = "black", size = 12, face = "plain"),
        axis.text.x = element_blank(),
        legend.position = "none",
        panel.grid = element_blank())+coord_flip()
p2
###############################################################
p3 <- ggplot(pcoadata, aes(group, PC2))+
  geom_boxplot(aes(fill=group, alpha = 0.1), outlier.colour = NA)+
  scale_fill_manual(values = c("tomato","orange","steelblue","darkgreen"))+
  geom_text(data = res, aes(x=group, y=df2, label = PC2),
            size = 5, color = "black", fontface = "plain")+
  theme(panel.background = element_rect(fill = "white", colour = "black"), 
        axis.ticks.length = unit(0.4, "lines"),
        axis.ticks = element_line(colour = "black"),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(colour = "black", size = 12,
                                   angle = 90, vjust = 0.5, 
                                   hjust = 0.5, face = "plain"),
        axis.text.y = element_blank(),
        legend.position = "none",
        panel.grid = element_blank())
p3
############################################  
p4 <- ggplot(pcoadata,aes(PC1, PC2))+
  geom_text(aes(x = -0.5,y = 0.6,
                label = paste("PERMANOVA:\ndf = ",otu.adonis$Df[1],"\nR2 = ",
                              round(otu.adonis$R2[1],4),"\np-value = ",
                              otu.adonis$`Pr(>F)`[1],
                              sep = "")),size = 3,family = "sans",fontface = 2)+
  theme_bw() + xlab(NULL) + ylab(NULL) +
  theme(panel.grid = element_blank(), 
        axis.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
p4  
####################################################

p <- p2+p4+p1+p3 + plot_layout(heights = c(1,3),widths = c(3,1),ncol = 2,nrow = 2)
p  
ggsave(plot = p,"Fig.2B.pdf",dpi = 600,width = 180,height = 180, units = "mm")  

```
## Fig.2CD. Network analysis

This section describes feature selection based on prevalence and relative abundance, with thresholds set to 0.75 and 0.0005, respectively. Ultimately, 344 features were retained for subsequent network construction. We further analyzed the topological characteristics of microbial networks across different host groups. The networks of centenarians and the elderly contained substantially more interacting edges than those of young individuals and Offspring. We then identified 273 nodes with consistent interaction patterns, meaning paired nodes maintained either positive or negative correlations across all networks. Among them, 256 nodes belonging to the largest modules were defined as core gut microbes. These microbes are likely key contributors to host health and longevity in the studied cohort.

```{r Network analysis. Abundance and prevalence thresholds selection as well as matrix preparation for correlation and p-value calculation)}
# step 1. load the count table generated from coverm
library(Hmisc)
library(igraph)
# MAG table：columns are samples，rows are MAGs， magtab.txt table were rarefied from the original count table
MAG_table_raw <- read.table("./data_fig2/magtab.txt", fill = T, check.names = F, row.names = 1, header=T, sep="\t") 
# This is the rarefied count table of that generated from Coverm software.
# In the table, the counts of sequences in all samples were re-sampled to 1,978,028.
# Load MAG taxonomic table.
tax_table_raw <- read.table("./data_fig2/drep95_annotation.txt", fill = T, check.names = F, row.names = 1, header=T, sep="\t")
# Load metadata of the samples.
meta_table_raw <- read.table("./data_fig2/metadata_rmNA.txt", fill = T, check.names = F, row.names = 1, header = T, sep = "\t")
###########################################################################################
MAG_table_c<-MAG_table_raw[,c(rownames(meta_table_raw[meta_table_raw$Group == "C",]))]
MAG_table_l<-MAG_table_raw[,c(rownames(meta_table_raw[meta_table_raw$Group == "L",]))]
MAG_table_e<-MAG_table_raw[,c(rownames(meta_table_raw[meta_table_raw$Group == "E",]))]
MAG_table_y<-MAG_table_raw[,c(rownames(meta_table_raw[meta_table_raw$Group == "Y",]))]
###########################################################################################
# MAG prevalence and abundance threshold selection, we follow the reference：https://doi.org/10.1016/j.cell.2024.09.019
MAG_tab_c <- t(MAG_table_c)
MAG_tab_l <- t(MAG_table_l)
MAG_tab_e <- t(MAG_table_e)
MAG_tab_y <- t(MAG_table_y)
# Calculate the prevalence of MAGs in samples across different groups (i.e. C-L-E-Y)
prev_prop_df_c <- apply(X = MAG_tab_c, MARGIN = 2,
               FUN = function(x){sum(x > 0)/dim(MAG_tab_c)[1]})

prev_prop_df_l <- apply(X = MAG_tab_l, MARGIN = 2,
                        FUN = function(x){sum(x > 0)/dim(MAG_tab_l)[1]})

prev_prop_df_e <- apply(X = MAG_tab_e,  MARGIN = 2,
                        FUN = function(x){sum(x > 0)/dim(MAG_tab_e)[1]})

prev_prop_df_y <- apply(X = MAG_tab_y,  MARGIN = 2,
                        FUN = function(x){sum(x > 0)/dim(MAG_tab_y)[1]})
################################################################
df_c<-data.frame(prev_prop_df_c)
df_l<-data.frame(prev_prop_df_l)
df_e<-data.frame(prev_prop_df_e)
df_y<-data.frame(prev_prop_df_y)
#########################################
## Prevalence curve 
########################################
# Function to calculate prevalence
calculate_prevalence <- function(data, group_name) {
  thresholds <- seq(0.01, 1, by = 0.01)
  prevalence <- sapply(thresholds, function(threshold) sum(data > threshold))
  data.frame(threshold = thresholds, prevalence = prevalence, group = group_name)
}
# Calculate prevalence for each group
C <- calculate_prevalence(df_c$prev_prop_df_c, "C")
L <- calculate_prevalence(df_l$prev_prop_df_l, "L")
E <- calculate_prevalence(df_e$prev_prop_df_e, "E")
Y <- calculate_prevalence(df_y$prev_prop_df_y, "Y")

# Combine all results into one data frame if needed
results <- rbind(C, L, E, Y)
results<-data.frame(results)
results$group<-factor(results$group,levels=c("C","L","E","Y"))
#####################################################
# Abundance curve
######################################################
# Calculate the abundance of each MAG in all samples.
total_relative_abundance = colSums(t(MAG_table_raw))/sum(colSums(t(MAG_table_raw)))
df_relative<-data.frame(total_relative_abundance)
options(scipen = 999)
range(df_relative$total_relative_abundance)
############################################
# Function to calculate ralative_abundance
calculate_rela <- function(data, group_name) {
  thresholds <- seq(0, 0.074, by = 0.00025)
  species <- sapply(thresholds, function(threshold) sum(data > threshold))
  data.frame(threshold = thresholds, species = species, group = group_name)
}
# Calculate abundance of MAGs in all samples.
DF_relative <- calculate_rela(df_relative,"Total")
DF_relative$threshold<- 100*DF_relative$threshold
#####################################################################
# step 2. Threshold used for selection of dominant species
# Following the reference aformented, we firstly took the MAGs that have prevalence more than 75% in each group for further selection.
is.above.prev <- prev_prop_df_c > 0.75 & prev_prop_df_l > 0.75 & prev_prop_df_e >0.75 & prev_prop_df_y > 0.75
table(is.above.prev)
###########################################################################
# Select the most abundant species(relative abundance > 0.0005)
total_relative_abundance = colSums(t(MAG_table_raw))/sum(colSums(t(MAG_table_raw)))
# Select the MAGs with relative_abundance > 0.0005.
is.above.abundance <- total_relative_abundance > 0.0005
table(is.above.abundance)
# Select the intersection MAGs on the basis of relative_abundance > 0.0005 & prevalence > 75% in each group.
table(is.above.prev & is.above.abundance)
target_MAG <- rownames(MAG_table_raw)[is.above.prev & is.above.abundance]
length(target_MAG)
##########################################################################
# Check the total reads number ratio of the selected dominant MAGs in all of the 306 samples.
target_MAG_table <- MAG_table_raw[target_MAG,]
reads_ratio_left <- sum(colSums(target_MAG_table))/sum(colSums(MAG_table_raw))
reads_ratio_left  # 83.60%
####################################################################
# We noticed that most (75%) species with a high prevalence in samples of this cohort, and at the same time, when we choose the 0.0005 as the threshold, the species drop slowly than the threshold before, and the remain species with a large amount of sequences count (83.60%), this proportion is convincing that these MAGs (representative species) could represent the dominant member of the gut bacterial community.

# Step 3. Species selection for FastSpar network calculation.

# Write out the MAG tables for further co-abundance association calculation use FastSpar, the calculated association table and their p-value table were further load into the present workspace for network construction using igraph R package.
# Original table including all the 306 samples.

target_MAG_table <- MAG_table_raw[target_MAG,]
dir.create("./data_fig2")
write.table(target_MAG_table,"data_fig2/MAG_tab_for_FastSpar.txt",row.names = T, sep = "\t")
## Centenarians
target_MAG_table_c <- MAG_table_c[target_MAG,]
write.table(target_MAG_table_c,"data_fig2/MAG_tab_for_FastSpar_c.txt",row.names = T, sep = "\t")
## Offspring
target_MAG_table_l <- MAG_table_l[target_MAG,]
write.table(target_MAG_table_l,"data_fig2/MAG_tab_for_FastSpar_l.txt",row.names = T, sep = "\t")
## Elderly
target_MAG_table_e <- MAG_table_e[target_MAG,]
write.table(target_MAG_table_e,"data_fig2/MAG_tab_for_FastSpar_e.txt",row.names = T, sep = "\t")
## Young
target_MAG_table_y <- MAG_table_y[target_MAG,]
write.table(target_MAG_table_y,"data_fig2/MAG_tab_for_FastSpar_y.txt",row.names = T, sep = "\t")
```
## Fig.2C, Network construction of the dominant prokaryotic species (MAGs) in the gut of different groups.
Here, we load the correlation and their corresponding p-value matrix calculated using the FastSpar software.
(1) Network of the gut prokaryotes of the centenarians

```{r Network analysis (Network construction of the gut prokaryotes of the centenarians)}
#####################################################################
# Step 4. Matrix input and network construction of prokaryotes in centenarian
# Calculate the relative abundance of MAGs within centenarian group.
total_relative_abundance_c = colSums(t(MAG_table_c))/sum(colSums(t(MAG_table_c)))
correlation_matrix_r<- read.table("./FastSpar_mydata/median_correlation_c.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r)<- 0
correlation_matrix_p<- read.table("./FastSpar_mydata/pvalues_c.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
# Thresholding: Retain only significant correlations
correlation_threshold <- 0 # Adjust as needed
p_threshold <- 0.001  # Adjust as needed

# Function to generate network table.
CorrDF <- function(cormat, pmat) {
  ut <- upper.tri(cormat) # upper triangle data
  data.frame(
    source = rownames(cormat)[col(cormat)[ut]],
    target = rownames(cormat)[row(cormat)[ut]],
    corr = (cormat)[ut],
    weight = abs((cormat)[ut]), # absolute value of association 
                                # coefficient as weight for each MAG pairs.
    p = pmat[ut],
    p.adjust = p.adjust(pmat[ut], method="none"), 
    # since the p-value matrix have been adjusted previously in FastSpar,
    # here, we don't have to adust the p-value.
    cor_type = ifelse((cormat)[ut]> 0, "Positive", "Negative")
  )
}

cor_df <- CorrDF(correlation_matrix_r , correlation_matrix_p) 
# generate the data table.

# use which() to index the correlated pairs and remove NA.
significant_cor_df <- cor_df[which(cor_df$weight >= correlation_threshold & cor_df$p.adjust <= p_threshold),] 
# remaining the edges with spearman absolute value >0.7 & q-value < 0.001
table(significant_cor_df$cor_type)
# unweighted network
g <- graph_from_data_frame(significant_cor_df, directed=F)
#################################################################################
# Check the nodes composition in each networks.
target_MAG_final_table<-MAG_table_raw[V(g)$name,]
# View(target_MAG_final_table)
dim(target_MAG_final_table) # 328 306

# calculate the counts ratio of the dominant MAGs (328) in all samples.
MAG_core_reads_ratio <- sum(colSums(target_MAG_final_table))/sum(colSums(MAG_table_raw))
MAG_core_reads_ratio # group C：83.10%；
##################################################################################
significant_tax <- tax_table_raw[V(g)$name,]
significant_tax$Abundance <- total_relative_abundance_c[V(g)$name]
####################################################################################
# plot_network(g, ps.prop_above_prev_abund, type = 'taxa', color = "Phylum")
V(g)$Domain <- significant_tax$Domain                            
V(g)$Phylum <- significant_tax$Phylum                              
V(g)$Class <- significant_tax$Class                                
V(g)$Order <- significant_tax$Order                                
V(g)$Family <- significant_tax$Family                              
V(g)$Genus <- significant_tax$Genus                                
V(g)$Species <- significant_tax$Species                            
V(g)$Abundance <- significant_tax$Abundance                          
# Create nodes list
node_list <- data.frame(node_id = names(V(g)),significant_tax)

# Create edges list
edge_list <- data.frame(edge_id = paste0("edge_", c(1:length(E(g)))),  significant_cor_df)

table(edge_list$cor_type)

# Network analysis

nodes_num = length(V(g))                   # nodes number
nodes_num # 328

edges_num = length(E(g))                   # edges number
edges_num # 11743

positive.corr_num = sum(E(g)$corr>0)        # positive edges number
positive.corr_num # 6263

positive.corr_prop = positive.corr_num/edges_num 
# ratio of positive edges in all edges.
positive.corr_prop # 0.533339

negative.corr_num = sum(E(g)$corr<0)        # negative edges number
negative.corr_num # 5480

negative.corr_prop = negative.corr_num/edges_num 
# ratio of the negative edges in all edges.
negative.corr_prop # 0.466661

average_degree = mean(degree(g))           # average degree
average_degree # 71.60366

average_shortest_path_length = mean_distance(g, directed = FALSE)     
# average shortest path length
average_shortest_path_length # 0.6849

network_diameter = diameter(g, directed = FALSE)                   
# network diameter
network_diameter # 1.694

network_density = edge_density(g)                                 
# network density
network_density # 0.2189714

modularity = modularity(g, membership(cluster_louvain(g)), directed = F) 
# network modularity
modularity # 0.253785

# transitivity：Transitivity measures the probability that the adjacent vertices of a vertex are connected. This is sometimes also called the clustering coefficient.
# clustering coefficient
clustering_coefficient <- transitivity(g, type="global")
clustering_coefficient # 0.6405

# Components
Components <- components(g)
Compts<-Components$no
Compts # 1
# module composition
comps_size <- sort(components(g)$csize, decreasing = TRUE)
comps_size
## Largest component
largest.comp<-V(g)[which.max(Components$csize)==Components$membership]
# largest.comp
MAG_largest_comp<-names(largest.comp)
# MAG_largest_comp
#############################################################################
##   MAG_largest_comp # used for MAG selection in the largest module.
####################################################################################
# Articulation points
Articulation_Points<-articulation_points(g)
Articulation_Points
AP<-Articulation_Points

length(AP)
network_parameter = data.frame(nodes_num, 
                               edges_num, 
                               positive.corr_num,
                               positive.corr_prop,
                               negative.corr_num,
                               negative.corr_prop,
                               average_degree,
                               average_shortest_path_length,
                               network_diameter, 
                               network_density,
                               clustering_coefficient,
                               modularity,
                               Compts
)

dir.create("./FastSpar_mydata/result_group_C")
output_dir = "./FastSpar_mydata/result_group_C"

write.table(node_list, file = file.path(output_dir, "network.node_list_c.tsv"), sep = "\t", quote = F, row.names = F)
write.table(edge_list, file = file.path(output_dir, "network.edge_list_c.tsv"), sep = "\t", quote = F, row.names = F)
write.table(network_parameter, file = file.path(output_dir, "network_parameter_c.tsv"), sep = "\t", quote = F, row.names = F)
write_graph(g, file.path(output_dir, 'network_c.graphml'), format = 'graphml')  # used for visualization in Gephi, here we use the Cotoscape to visualize the result using the "network.node_list.tsv" and "network.edge_list.tsv" files.
```
(2) Network of the gut prokaryotes of the Offspring

```{r Network analysis (Network construction of the gut prokaryotes of the lineal descendants of the centenarians)}
# Step 5. Matrix input and network construction of prokaryotes in lineal descendants.
# Offspring
total_relative_abundance_l <- colSums(t(MAG_table_l))/sum(colSums(t(MAG_table_l)))
correlation_matrix_r<- read.table("./FastSpar_mydata/median_correlation_l.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r)<- 0
correlation_matrix_p<- read.table("./FastSpar_mydata/pvalues_l.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")

# Thresholding: Retain only significant correlations
correlation_threshold <- 0 # Adjust as needed
p_threshold <- 0.001  # Adjust as needed

CorrDF <- function(cormat, pmat) {
  ut <- upper.tri(cormat) # upper triangle.
  data.frame(
    source = rownames(cormat)[col(cormat)[ut]],
    target = rownames(cormat)[row(cormat)[ut]],
    corr = (cormat)[ut],
    weight = abs((cormat)[ut]), # weights of edges.
    p = pmat[ut],
    p.adjust = p.adjust(pmat[ut], method="none"), 
    cor_type = ifelse((cormat)[ut]> 0, "Positive", "Negative")
  )
}

cor_df <- CorrDF(correlation_matrix_r , correlation_matrix_p) # 

significant_cor_df <- cor_df[which(cor_df$weight >= correlation_threshold & cor_df$p.adjust <= p_threshold),] 
table(significant_cor_df$cor_type)

g <- graph_from_data_frame(significant_cor_df, directed=F)
############################################################################
target_MAG_final_table<-MAG_table_raw[V(g)$name,]
# View(target_MAG_final_table)
dim(target_MAG_final_table) # 324 306

MAG_core_reads_ratio <- sum(colSums(target_MAG_final_table))/sum(colSums(MAG_table_raw))
MAG_core_reads_ratio # group L：82.46%; 
##################################################################################
significant_tax <- tax_table_raw[V(g)$name,]
significant_tax$Abundance <- total_relative_abundance_l[V(g)$name] 
####################################################################################
# plot_network(g, ps.prop_above_prev_abund, type = 'taxa', color = "Phylum")
V(g)$Domain <- significant_tax$Domain                          
V(g)$Phylum <- significant_tax$Phylum                             
V(g)$Class <- significant_tax$Class                               
V(g)$Order <- significant_tax$Order                               
V(g)$Family <- significant_tax$Family                             
V(g)$Genus <- significant_tax$Genus                               
V(g)$Species <- significant_tax$Species                            
V(g)$Abundance <- significant_tax$Abundance                         
# Nodes list
node_list <- data.frame(node_id = names(V(g)),significant_tax)

# Edges list
edge_list <- data.frame(edge_id = paste0("edge_", c(1:length(E(g)))),  significant_cor_df)

table(edge_list$cor_type) # 1965 Neg, 3510 Pos

# Network analysis

nodes_num = length(V(g))                   # nodes number
nodes_num # 324

edges_num = length(E(g))                   # edges number
edges_num # 5475

positive.corr_num = sum(E(g)$corr>0)        # positive edges number
positive.corr_num # 3510

positive.corr_prop = positive.corr_num/edges_num 
# ratio of the positive edges in all samples.
positive.corr_prop # 64.11%

negative.corr_num = sum(E(g)$corr<0)        # negative edges number
negative.corr_num # 1965

negative.corr_prop = negative.corr_num/edges_num 
# ratio of the negative edges in all samples.
negative.corr_prop # 35.89%

average_degree = mean(degree(g))           
# average degree
average_degree # 33.80%

average_shortest_path_length = mean_distance(g, directed = FALSE)   

average_shortest_path_length # 1.07

network_diameter = diameter(g, directed = FALSE)             
network_diameter # 3.15

network_density = edge_density(g)                               
network_density # 0.1046

modularity = modularity(g, membership(cluster_louvain(g)), directed = F)
modularity # 0.4069428

# Transitivity：transitivity measures the probability that the adjacent vertices of a vertex are connected. This is sometimes also called the clustering coefficient.
# clustering coefficient
clustering_coefficient <- transitivity(g, type="global")
clustering_coefficient # 0.4825963

# Components
Components <- components(g)
Compts<-Components$no
Compts # 1

comps_size <- sort(components(g)$csize, decreasing = TRUE)
comps_size
## Largest component
largest.comp<-V(g)[which.max(Components$csize)==Components$membership]
# largest.comp
MAG_largest_comp<-names(largest.comp)
# MAG_largest_comp
############################################################################
# Articulation points
Articulation_Points<-articulation_points(g)
Articulation_Points
AP<-Articulation_Points

length(AP)
network_parameter = data.frame(nodes_num, 
                               edges_num, 
                               positive.corr_num,
                               positive.corr_prop,
                               negative.corr_num,
                               negative.corr_prop,
                               average_degree,
                               average_shortest_path_length,
                               network_diameter, 
                               network_density,
                               clustering_coefficient,
                               modularity,
                               Compts
)
dir.create("./FastSpar_mydata/result_group_L")
output_dir = "./FastSpar_mydata/result_group_L"

write.table(node_list, file = file.path(output_dir, "network.node_list_l.tsv"), sep = "\t", quote = F, row.names = F)
write.table(edge_list, file = file.path(output_dir, "network.edge_list_l.tsv"), sep = "\t", quote = F, row.names = F)
write.table(network_parameter, file = file.path(output_dir, "network_parameter_l.tsv"), sep = "\t", quote = F, row.names = F)
write_graph(g, file.path(output_dir, 'network_l.graphml'), format = 'graphml')
```
(3) Network of the gut prokaryotes of the elderly.

```{r Network analysis (Network construction of the gut prokaryotes of the elderly)}
# Step 6. Matrix input and network construction of prokaryotes in the elderly
# Elderly
total_relative_abundance_e = colSums(t(MAG_table_e))/sum(colSums(t(MAG_table_e)))
# load data table
correlation_matrix_r<- read.table("./FastSpar_mydata/median_correlation_e.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r)<- 0
correlation_matrix_p<- read.table("./FastSpar_mydata/pvalues_e.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")

# Thresholding: Retain only significant correlations
correlation_threshold <- 0 # Adjust as needed
p_threshold <- 0.001  # Adjust as needed

CorrDF <- function(cormat, pmat) {
  ut <- upper.tri(cormat) # upper triangle
  data.frame(
    source = rownames(cormat)[col(cormat)[ut]],
    target = rownames(cormat)[row(cormat)[ut]],
    corr = (cormat)[ut],
    weight = abs((cormat)[ut]), # edges weights
    p = pmat[ut],
    p.adjust = p.adjust(pmat[ut], method="none"), 
    cor_type = ifelse((cormat)[ut]> 0, "Positive", "Negative")
  )
}

cor_df <- CorrDF(correlation_matrix_r , correlation_matrix_p) # 

significant_cor_df <- cor_df[which(cor_df$weight >= correlation_threshold & cor_df$p.adjust <= p_threshold),] 
table(significant_cor_df$cor_type) # 4272 Neg, 5042 Pos

g <- graph_from_data_frame(significant_cor_df, directed=F)
#################################################################################
# Check the nodes composition.
target_MAG_final_table<-MAG_table_raw[V(g)$name,]
# View(target_MAG_final_table)
dim(target_MAG_final_table) # 325
# calculate reads ratio in the total reads.
MAG_core_reads_ratio <- sum(colSums(target_MAG_final_table))/sum(colSums(MAG_table_raw))
MAG_core_reads_ratio # E组：82.65% ; 
##################################################################################
significant_tax <- tax_table_raw[V(g)$name,]
significant_tax$Abundance <- total_relative_abundance_e[V(g)$name] 
############################################################################
# plot_network(g, ps.prop_above_prev_abund, type = 'taxa', color = "Phylum")
V(g)$Domain <- significant_tax$Domain                            
V(g)$Phylum <- significant_tax$Phylum                              
V(g)$Class <- significant_tax$Class                                
V(g)$Order <- significant_tax$Order                                
V(g)$Family <- significant_tax$Family                             
V(g)$Genus <- significant_tax$Genus                                
V(g)$Species <- significant_tax$Species                            
V(g)$Abundance <- significant_tax$Abundance                         
# nodes list
node_list <- data.frame(node_id = names(V(g)),significant_tax)

# edges list
edge_list <- data.frame(edge_id = paste0("edge_", c(1:length(E(g)))),  significant_cor_df)
table(edge_list$cor_type) # 4272 Neg, 5042 Pos

# Network analysis
nodes_num = length(V(g))                   # nodes number
nodes_num # 325

edges_num = length(E(g))                   # edges number
edges_num # 9314

positive.corr_num = sum(E(g)$corr>0)        # positive edges number
positive.corr_num # 5042

positive.corr_prop = positive.corr_num/edges_num 
# ratio of the positive edges in all edges.
positive.corr_prop # 54.13%

negative.corr_num = sum(E(g)$corr<0)        # negative edges number
negative.corr_num # 4272

negative.corr_prop = negative.corr_num/edges_num 
# ratio of the negative edges number in all edges.
negative.corr_prop # 0.4586644

average_degree = mean(degree(g))           # average degree
average_degree # 57.31692

average_shortest_path_length = mean_distance(g, directed = FALSE)   
average_shortest_path_length # 0.8919869

network_diameter = diameter(g, directed = FALSE)                  
network_diameter # 2.5791

network_density = edge_density(g)                               
network_density # 0.1769041

modularity = modularity(g, membership(cluster_louvain(g)), directed = F) 
modularity # 0.2337847

# Transitivity: transitivity measures the probability that the adjacent vertices of a vertex are connected. This is sometimes also called the clustering coefficient.
# clustering coefficient
clustering_coefficient <- transitivity(g, type="global")
clustering_coefficient # 0.5884461

# Components
Components <- components(g)
Compts<-Components$no
Compts # 1

comps_size <- sort(components(g)$csize, decreasing = TRUE)
comps_size # 325
## Largest component
largest.comp<-V(g)[which.max(Components$csize)==Components$membership]
largest.comp
MAG_largest_comp<-names(largest.comp)
# MAG_largest_comp
############################################################################
# Articulation points
Articulation_Points<-articulation_points(g)
Articulation_Points
AP<-Articulation_Points

length(AP)
network_parameter = data.frame(nodes_num, 
                               edges_num, 
                               positive.corr_num,
                               positive.corr_prop,
                               negative.corr_num,
                               negative.corr_prop,
                               average_degree,
                               average_shortest_path_length,
                               network_diameter, 
                               network_density,
                               clustering_coefficient,
                               modularity,
                               Compts
)
dir.create("./FastSpar_mydata/result_group_E")
output_dir = "./FastSpar_mydata/result_group_E"

write.table(node_list, file = file.path(output_dir, "network.node_list_e.tsv"), sep = "\t", quote = F, row.names = F)
write.table(edge_list, file = file.path(output_dir, "network.edge_list_e.tsv"), sep = "\t", quote = F, row.names = F)
write.table(network_parameter, file = file.path(output_dir, "network_parameter_e.tsv"), sep = "\t", quote = F, row.names = F)
write_graph(g, file.path(output_dir, 'network_e.graphml'), format = 'graphml')
```
(4) Network of the gut prokaryotes of the young

```{r network analysis (Stage-5: Network construction of the gut prokaryotes of the Non-lineal young)}
# Step 7. Matrix input and network construction of prokaryotes in the young
total_relative_abundance_y = colSums(t(MAG_table_y))/sum(colSums(t(MAG_table_y)))
# Load data table
correlation_matrix_r<- read.table("./FastSpar_mydata/median_correlation_y.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r)<- 0
correlation_matrix_p<- read.table("./FastSpar_mydata/pvalues_y.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")

# Thresholding: Retain only significant correlations
correlation_threshold <- 0 # Adjust as needed
p_threshold <- 0.001  # Adjust as needed 0.05 有点太

CorrDF <- function(cormat, pmat) {
  ut <- upper.tri(cormat) # upper triangle
  data.frame(
    source = rownames(cormat)[col(cormat)[ut]],
    target = rownames(cormat)[row(cormat)[ut]],
    corr = (cormat)[ut],
    weight = abs((cormat)[ut]), # association weights
    p = pmat[ut],
    p.adjust = p.adjust(pmat[ut], method="none"), 
    cor_type = ifelse((cormat)[ut]> 0, "Positive", "Negative")
  )
}

cor_df <- CorrDF(correlation_matrix_r , correlation_matrix_p) 

significant_cor_df <- cor_df[which(cor_df$weight >= correlation_threshold & cor_df$p.adjust <= p_threshold),] 
table(significant_cor_df$cor_type) # 2003 Neg, 3617 Pos

g <- graph_from_data_frame(significant_cor_df, directed=F)
#################################################################################
target_MAG_final_table<-MAG_table_raw[V(g)$name,]
# View(target_MAG_final_table)
dim(target_MAG_final_table) # 319 306
# reads ratio of the nodes in the network in all samples.
MAG_core_reads_ratio <- sum(colSums(target_MAG_final_table))/sum(colSums(MAG_table_raw))
MAG_core_reads_ratio # group Y：82.15%
##################################################################################
significant_tax <- tax_table_raw[V(g)$name,]
significant_tax$Abundance <- total_relative_abundance_y[V(g)$name] 
####################################################################################
# plot_network(g, ps.prop_above_prev_abund, type = 'taxa', color = "Phylum")
V(g)$Domain <- significant_tax$Domain                            
V(g)$Phylum <- significant_tax$Phylum                             
V(g)$Class <- significant_tax$Class                               
V(g)$Order <- significant_tax$Order                              
V(g)$Family <- significant_tax$Family                           
V(g)$Genus <- significant_tax$Genus                             
V(g)$Species <- significant_tax$Species                         
V(g)$Abundance <- significant_tax$Abundance                     
# nodes list
node_list <- data.frame(node_id = names(V(g)),significant_tax)

# edges list
edge_list <- data.frame(edge_id = paste0("edge_", c(1:length(E(g)))),  significant_cor_df)

table(edge_list$cor_type) # 2003 Neg, 3617 Pos

# Network analysis

nodes_num = length(V(g))                   # nodes number
nodes_num # 319 

edges_num = length(E(g))                   # edges number
edges_num # 5620

positive.corr_num = sum(E(g)$corr>0)        # positive edges number
positive.corr_num # 3617

positive.corr_prop = positive.corr_num/edges_num 
# ratio of the positive edges in all edges.
positive.corr_prop # 64.36%

negative.corr_num = sum(E(g)$corr<0)        # negative edges number
negative.corr_num # 2003

negative.corr_prop = negative.corr_num/edges_num 
# ratio of the negative edges in all edges.
negative.corr_prop # 35.64%

average_degree = mean(degree(g))          
average_degree # 35.24

average_shortest_path_length = mean_distance(g, directed = FALSE)     
average_shortest_path_length # 1.058399

network_diameter = diameter(g, directed = FALSE)                  
network_diameter # 2.8987

network_density = edge_density(g)                                
network_density # 0.1108

modularity = modularity(g, membership(cluster_louvain(g)), directed = F) 
modularity # 0.3674

# Transitivity：transitivity measures the probability that the adjacent vertices of a vertex are connected. This is sometimes also called the clustering coefficient.
# clustering coefficient
clustering_coefficient <- transitivity(g, type="global")
clustering_coefficient # 0.5330604

# Components
Components <- components(g)
Compts<-Components$no
Compts # 1

comps_size <- sort(components(g)$csize, decreasing = TRUE)
comps_size # 319
## Largest component
largest.comp<-V(g)[which.max(Components$csize)==Components$membership]
# largest.comp
MAG_largest_comp<-names(largest.comp)
# MAG_largest_comp
############################################################################
# Articulation points
Articulation_Points<-articulation_points(g)
Articulation_Points
AP<-Articulation_Points

length(AP)
network_parameter = data.frame(nodes_num, 
                               edges_num, 
                               positive.corr_num,
                               positive.corr_prop,
                               negative.corr_num,
                               negative.corr_prop,
                               average_degree,
                               average_shortest_path_length,
                               network_diameter, 
                               network_density,
                               clustering_coefficient,
                               modularity,
                               Compts
)
dir.create("./FastSpar_mydata/result_group_Y")
output_dir = "./FastSpar_mydata/result_group_Y"

write.table(node_list, file = file.path(output_dir, "network.node_list_y.tsv"), sep = "\t", quote = F, row.names = F)
write.table(edge_list, file = file.path(output_dir, "network.edge_list_y.tsv"), sep = "\t", quote = F, row.names = F)
write.table(network_parameter, file = file.path(output_dir, "network_parameter_y.tsv"), sep = "\t", quote = F, row.names = F)
write_graph(g, file.path(output_dir, 'network_y.graphml'), format = 'graphml')
```
(5) Venn diagram analysis across groups

```{r Venndiagram analysis (Stage-6: The selection of the consistently interacted gut prokaryotes across different groups)}
# calculate relative abundance MAGs in each group.
total_relative_abundance_c <- colSums(t(MAG_table_c))/sum(colSums(t(MAG_table_c)))
total_relative_abundance_l <- colSums(t(MAG_table_l))/sum(colSums(t(MAG_table_l)))
total_relative_abundance_e <- colSums(t(MAG_table_e))/sum(colSums(t(MAG_table_e)))
total_relative_abundance_y <- colSums(t(MAG_table_y))/sum(colSums(t(MAG_table_y)))
total_relative_abundance <- colSums(t(MAG_table_raw))/sum(colSums(t(MAG_table_raw)))
#################################################################################
# Load the correlation matrix and their corresponding p-value matrix
##################################################################
correlation_matrix_r_C<- read.table("./FastSpar_mydata/median_correlation_c.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r_C)<- 0
correlation_matrix_p_C<- read.table("./FastSpar_mydata/pvalues_c.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
#####################################################################
correlation_matrix_r_L<- read.table("./FastSpar_mydata/median_correlation_l.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r_L)<- 0
correlation_matrix_p_L<- read.table("./FastSpar_mydata/pvalues_l.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
######################################################################
correlation_matrix_r_E<- read.table("./FastSpar_mydata/median_correlation_e.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r_E)<- 0
correlation_matrix_p_E<- read.table("./FastSpar_mydata/pvalues_e.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
#####################################################################
correlation_matrix_r_Y<- read.table("./FastSpar_mydata/median_correlation_y.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r_Y)<- 0
correlation_matrix_p_Y<- read.table("./FastSpar_mydata/pvalues_y.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
#####################################################################
# correlation and its p-value matrix on all samples.
correlation_matrix_r<- read.table("./FastSpar_mydata/median_correlation.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r)<- 0
correlation_matrix_p<- read.table("./FastSpar_mydata/pvalues.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
#####################################################################
# Thresholding: Retain only significant correlations
correlation_threshold <- 0 # Adjust as needed
p_threshold <- 0.001  # Adjust as needed

CorrDF <- function(cormat, pmat) {
  ut <- upper.tri(cormat) # upper triangle
  data.frame(
    source = rownames(cormat)[col(cormat)[ut]],
    target = rownames(cormat)[row(cormat)[ut]],
    corr = (cormat)[ut],
    weight = abs((cormat)[ut]), # correlation weights
    p = pmat[ut],
    p.adjust = p.adjust(pmat[ut], method="none"), 
    cor_type = ifelse((cormat)[ut]> 0, "Positive", "Negative")
  )
}
##################################################################
cor_df_C <- CorrDF(correlation_matrix_r_C, correlation_matrix_p_C) 
dim(cor_df_C)
# 54285 pairs
cor_df_L <- CorrDF(correlation_matrix_r_L, correlation_matrix_p_L)
dim(cor_df_L)
# 54285 pairs
cor_df_E <- CorrDF(correlation_matrix_r_E, correlation_matrix_p_E)
dim(cor_df_E)
# 54285 pairs
cor_df_Y <- CorrDF(correlation_matrix_r_Y, correlation_matrix_p_Y)
dim(cor_df_Y)
# 54285 pairs
cor_df_whole<- CorrDF(correlation_matrix_r, correlation_matrix_p)
dim(cor_df_whole)
####################################################################
#generate a new column called pairs, concatenated with the columns of "source", "target", and the "cor_type" by "_".
cor_df_C$pairs <- paste(cor_df_C$source,cor_df_C$target,cor_df_C$cor_type, sep = "__")
cor_df_L$pairs <- paste(cor_df_L$source,cor_df_L$target,cor_df_L$cor_type, sep = "__")
cor_df_E$pairs <- paste(cor_df_E$source,cor_df_E$target,cor_df_E$cor_type, sep = "__")
cor_df_Y$pairs <- paste(cor_df_Y$source,cor_df_Y$target,cor_df_Y$cor_type, sep = "__")
cor_df_whole$pairs <- paste(cor_df_whole$source,cor_df_whole$target, cor_df_whole$cor_type, sep = "__")
####################################################################
significant_cor_df_C <- cor_df_C[which(cor_df_C$weight >= correlation_threshold & cor_df_C$p.adjust <= p_threshold),] 
table(significant_cor_df_C$cor_type) # 5480 Neg, 6263 Pos,
range(significant_cor_df_C$weight) # 0.259-0.946
############################################################
significant_cor_df_L <- cor_df_L[which(cor_df_L$weight >= correlation_threshold & cor_df_L$p.adjust <= p_threshold),]
table(significant_cor_df_L$cor_type) # 1965 Neg, 3510 Pos
range(significant_cor_df_L$weight) # 0.335-0.964
#############################################################
significant_cor_df_E <- cor_df_E[which(cor_df_E$weight >= correlation_threshold & cor_df_E$p.adjust <= p_threshold),]
table(significant_cor_df_E$cor_type) # 4272 Neg, 5042 Pos
range(significant_cor_df_E$weight) # 0.325-0.966
##############################################################
significant_cor_df_Y <- cor_df_Y[which(cor_df_Y$weight >= correlation_threshold & cor_df_Y$p.adjust <= p_threshold),]
table(significant_cor_df_Y$cor_type) # 2003 Neg, 3617 Pos
range(significant_cor_df_Y$weight)  # 0.330-0.975
##############################################################
significant_cor_df_whole <- cor_df_whole[which(cor_df_whole$weight >= correlation_threshold & cor_df_whole$p.adjust <= p_threshold),]
table(significant_cor_df_whole$cor_type) # 12311 Neg, 11117 Pos
range(significant_cor_df_whole$weight)
###############################################################
# Venndiagram analysis the unique pairs across groups for the positive edges.
Positive_C_tab <- significant_cor_df_C[which(significant_cor_df_C$cor_type== "Positive"),]
Positive_L_tab <- significant_cor_df_L[which(significant_cor_df_L$cor_type== "Positive"),]
Positive_E_tab <- significant_cor_df_E[which(significant_cor_df_E$cor_type== "Positive"),]
Positive_Y_tab <- significant_cor_df_Y[which(significant_cor_df_Y$cor_type== "Positive"),]
Positive_whole_tab<- significant_cor_df_whole[which(significant_cor_df_whole$cor_type=="Positive"),]
Positive_tab <-list("Positive_C"=Positive_C_tab$pairs,
                          "Positive_L"=Positive_L_tab$pairs,
                          "Positive_E"=Positive_E_tab$pairs,
                          "Positive_Y"=Positive_Y_tab$pairs)

#################################################################
# # Venndiagram analysis the unique pairs across groups for the negative edges.
Negative_C_tab <- significant_cor_df_C[which(significant_cor_df_C$cor_type == "Negative"),]
Negative_L_tab <- significant_cor_df_L[which(significant_cor_df_L$cor_type== "Negative"),]
Negative_E_tab <- significant_cor_df_E[which(significant_cor_df_E$cor_type == "Negative"),]
Negative_Y_tab <- significant_cor_df_Y[which(significant_cor_df_Y$cor_type== "Negative"),]

Negative_tab <-list("Negative_C"=Negative_C_tab$pairs,
                    "Negative_L"=Negative_L_tab$pairs,
                    "Negative_E"=Negative_E_tab$pairs,
                    "Negative_Y"=Negative_Y_tab$pairs)

```
(6) Consistently interacted community across groups

```{r Network analysis (Stage-7: core microbes across different networks)}
# Relative abundance calculation for the MAGs in each group.
total_relative_abundance_c = colSums(t(MAG_table_c))/sum(colSums(t(MAG_table_c)))
total_relative_abundance_l = colSums(t(MAG_table_l))/sum(colSums(t(MAG_table_l)))
total_relative_abundance_e = colSums(t(MAG_table_e))/sum(colSums(t(MAG_table_e)))
total_relative_abundance_y = colSums(t(MAG_table_y))/sum(colSums(t(MAG_table_y)))
total_relative_abundance =colSums(t(MAG_table_raw))/sum(colSums(t(MAG_table_raw)))
############################################################################
correlation_matrix_r_C<- read.table("./FastSpar_mydata/median_correlation_c.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r_C)<- 0
correlation_matrix_p_C<- read.table("./FastSpar_mydata/pvalues_c.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
#####################################################################
correlation_matrix_r_L<- read.table("./FastSpar_mydata/median_correlation_l.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r_L)<- 0
correlation_matrix_p_L<- read.table("./FastSpar_mydata/pvalues_l.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
######################################################################
correlation_matrix_r_E<- read.table("./FastSpar_mydata/median_correlation_e.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r_E)<- 0
correlation_matrix_p_E<- read.table("./FastSpar_mydata/pvalues_e.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
#####################################################################
correlation_matrix_r_Y<- read.table("./FastSpar_mydata/median_correlation_y.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r_Y)<- 0
correlation_matrix_p_Y<- read.table("./FastSpar_mydata/pvalues_y.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
#####################################################################
# correlation and p-value matrix of all samples.
correlation_matrix_r<- read.table("./FastSpar_mydata/median_correlation.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
diag(correlation_matrix_r)<- 0
correlation_matrix_p<- read.table("./FastSpar_mydata/pvalues.tsv",fill = T, check.names = F, row.names = 1, header=T, sep="\t")
#####################################################################
# Thresholding: Retain only significant correlations
correlation_threshold <- 0 # Adjust as needed
p_threshold <- 0.001  # Adjust as needed

CorrDF <- function(cormat, pmat) {
  ut <- upper.tri(cormat) # upper triangle
  data.frame(
    source = rownames(cormat)[col(cormat)[ut]],
    target = rownames(cormat)[row(cormat)[ut]],
    corr = (cormat)[ut],
    weight = abs((cormat)[ut]), 
    p = pmat[ut],
    p.adjust = p.adjust(pmat[ut], method="none"), 
    cor_type = ifelse((cormat)[ut]> 0, "Positive", "Negative")
  )
}
##################################################################
cor_df_C <- CorrDF(correlation_matrix_r_C, correlation_matrix_p_C) 
dim(cor_df_C)
# 54285 pairs
cor_df_L <- CorrDF(correlation_matrix_r_L, correlation_matrix_p_L)
dim(cor_df_L)
# 54285 pairs
cor_df_E <- CorrDF(correlation_matrix_r_E, correlation_matrix_p_E)
dim(cor_df_E)
# 54285 pairs
cor_df_Y <- CorrDF(correlation_matrix_r_Y, correlation_matrix_p_Y)
dim(cor_df_Y)
# 54285 pairs
cor_df_whole<- CorrDF(correlation_matrix_r, correlation_matrix_p)
dim(cor_df_whole)
####################################################################
#generate a new column called pairs, concatenated with the columns of "source", "target", and the "cor_type" by "_".
cor_df_C$pairs <- paste(cor_df_C$source,cor_df_C$target,cor_df_C$cor_type, sep = "__")
cor_df_L$pairs <- paste(cor_df_L$source,cor_df_L$target,cor_df_L$cor_type, sep = "__")
cor_df_E$pairs <- paste(cor_df_E$source,cor_df_E$target,cor_df_E$cor_type, sep = "__")
cor_df_Y$pairs <- paste(cor_df_Y$source,cor_df_Y$target,cor_df_Y$cor_type, sep = "__")
cor_df_whole$pairs <- paste(cor_df_whole$source,cor_df_whole$target, cor_df_whole$cor_type, sep = "__")
####################################################################
significant_cor_df_C <- cor_df_C[which(cor_df_C$weight >= correlation_threshold & cor_df_C$p.adjust <= p_threshold),] 
table(significant_cor_df_C$cor_type) # 5480 Neg, 6264 Pos,
range(significant_cor_df_C$weight) # 0.259-0.946
############################################################
significant_cor_df_L <- cor_df_L[which(cor_df_L$weight >= correlation_threshold & cor_df_L$p.adjust <= p_threshold),]
table(significant_cor_df_L$cor_type) # 1965 Neg, 3510 Pos
range(significant_cor_df_L$weight) # 0.335-0.964
#############################################################
significant_cor_df_E <- cor_df_E[which(cor_df_E$weight >= correlation_threshold & cor_df_E$p.adjust <= p_threshold),]
table(significant_cor_df_E$cor_type) # 4272 Neg, 5042 Pos
range(significant_cor_df_E$weight) # 0.325-0.966
##############################################################
significant_cor_df_Y <- cor_df_Y[which(cor_df_Y$weight >= correlation_threshold & cor_df_Y$p.adjust <= p_threshold),]
table(significant_cor_df_Y$cor_type) # 2003 Neg, 3617 Pos
range(significant_cor_df_Y$weight)  # 0.330-0.975
###############################################################
library(dplyr)
# Select the consistently associated pairs.
MAG_pairs <- intersect(significant_cor_df_C$pairs,significant_cor_df_L$pairs) %>% intersect(significant_cor_df_E$pairs) %>% intersect(significant_cor_df_Y$pairs)
length(MAG_pairs)
################################################################
significant_cor_df_whole <- cor_df_whole[which(cor_df_whole$weight >= correlation_threshold & cor_df_whole$p.adjust <= p_threshold),]
table(significant_cor_df_whole$cor_type) # 12311 Neg, 11117 Pos
range(significant_cor_df_whole$weight) # 0.148-0.965
######################################################################
# Select the core microbes (MAGs)
significant_cor_df_whole_final <- significant_cor_df_whole %>% filter(pairs %in% MAG_pairs)
table(significant_cor_df_whole_final$cor_type)  # 216 Neg, 1572 Pos
range(significant_cor_df_whole_final$weight)  # 0.3549-0.965
######################################################################
# construct the network of the core microbes.
g <- graph_from_data_frame(significant_cor_df_whole_final, directed=F)
#################################################################################
# check the node composition
target_MAG_final_table<-MAG_table_raw[V(g)$name,]
# View(target_MAG_final_table)
dim(target_MAG_final_table) # 273 306
# reads ratio of the selected core microbes in all samples.
MAG_core_reads_ratio <- sum(colSums(target_MAG_final_table))/sum(colSums(MAG_table_raw))
MAG_core_reads_ratio # reads ratio：73.98%
##################################################################################
significant_tax <- tax_table_raw[V(g)$name,]
significant_tax$Abundance <- total_relative_abundance[V(g)$name] #
###########################################################################
# plot_network(g, ps.prop_above_prev_abund, type = 'taxa', color = "Phylum")
V(g)$Domain <- significant_tax$Domain                            
V(g)$Phylum <- significant_tax$Phylum                             
V(g)$Class <- significant_tax$Class                              
V(g)$Order <- significant_tax$Order                              
V(g)$Family <- significant_tax$Family                            
V(g)$Genus <- significant_tax$Genus                              
V(g)$Species <- significant_tax$Species                         
V(g)$Abundance <- significant_tax$Abundance                       
# nodes list
node_list <- data.frame(node_id = names(V(g)),significant_tax)

# edge list
edge_list <- data.frame(edge_id = paste0("edge_", c(1:length(E(g)))),  significant_cor_df_whole_final)

table(edge_list$cor_type)
# 216 Negative, 1572 Positive
# Network analysis

nodes_num = length(V(g))                   # nodes number
nodes_num # 273

edges_num = length(E(g))                   # edges number
edges_num # 1788

positive.corr_num = sum(E(g)$corr>0)        # positive edges number
positive.corr_num # 1572

positive.corr_prop = positive.corr_num/edges_num 
# ratio of the positive edges in all edges.
positive.corr_prop # 87.92%

negative.corr_num = sum(E(g)$corr<0)        
# negative edges number
negative.corr_num # 216

negative.corr_prop = negative.corr_num/edges_num 
# ratio of the negative edges in all edges.
negative.corr_prop # 12.08%

average_degree = mean(degree(g))          
average_degree # 13.10

average_shortest_path_length = mean_distance(g, directed = FALSE)     
average_shortest_path_length # 1.98

network_diameter = diameter(g, directed = FALSE)                  
network_diameter # 5.19

network_density = edge_density(g)                              
network_density # 0.048

modularity = modularity(g, membership(cluster_louvain(g)), directed = F) 
modularity # 0.657

# Transitivity：transitivity measures the probability that the adjacent vertices of a vertex are connected. This is sometimes also called the clustering coefficient.
# Clustering coefficient
clustering_coefficient <- transitivity(g, type="global")
clustering_coefficient # 0.572

# Components
Components <- components(g)
Compts<-Components$no
Compts # 8

comps_size <- sort(components(g)$csize, decreasing = TRUE)
comps_size
## Largest component
largest.comp<-V(g)[which.max(Components$csize)==Components$membership]
# largest.comp
MAG_largest_comp<-names(largest.comp)
MAG_largest_comp[1:10]
#
dir.create("./FastSpar_mydata/result_whole/")
write.table(MAG_table_raw[MAG_largest_comp,], file="./FastSpar_mydata/result_whole/MAG_Largest_comp.tsv", sep = "\t", quote = F, row.names = T)
write.table(tax_table_raw[MAG_largest_comp,], file = "./FastSpar_mydata/result_whole/MAG_tax_table_core.tsv", sep = "\t", quote = F, row.names = T)
############################################################################
network_parameter = data.frame(nodes_num, 
                               edges_num, 
                               positive.corr_num,
                               positive.corr_prop,
                               negative.corr_num,
                               negative.corr_prop,
                               average_degree,
                               average_shortest_path_length,
                               network_diameter, 
                               network_density,
                               clustering_coefficient,
                               modularity,
                               Compts
)
dir.create("./FastSpar_mydata/result_common")
output_dir = "./FastSpar_mydata/result_common"

write.table(node_list, file = file.path(output_dir, "network.node_list_whole.tsv"), sep = "\t", quote = F, row.names = F)
write.table(edge_list, file = file.path(output_dir, "network.edge_list_whole.tsv"), sep = "\t", quote = F, row.names = F)
write.table(network_parameter, file = file.path(output_dir, "network_parameter_whole.tsv"), sep = "\t", quote = F, row.names = F)
write_graph(g, file.path(output_dir, 'network_whole.graphml'), format = 'graphml')  
```
## Fig.2E. Capability of the core microbiome in distinguish centenarian from the other volunteer individuals.
```{r}
# devtools::install_github("WandeRum/multiROC")
# devtools::install_github("cran/dummies")
library(multiROC)
library(randomForest)
library(nnet)
library(dummies)
library(ggplot2)
library(caret)

## data manipulation
## data separation
# load MAG table
MAG_tab<- read.table("./data_fig2/MAG_Largest_comp_grouped.tsv",fill = T, check.names = F, 
                     row.names = 1, header=T, sep="\t",stringsAsFactors = T)
set.seed(123456)
# 75% data as training data, 25% data left as testing data
trainIndex <- createDataPartition(MAG_tab$Group, p = 0.75, list = FALSE)
train_df <- MAG_tab[trainIndex, ]
test_df <- MAG_tab[-trainIndex, ]
nrow(train_df);nrow(test_df)

## machine learning
## random forest
################################################################################
# predicting centenarians or non-centenarians
MAG_tab$longevity<- ifelse(MAG_tab$Group == "C","C","other")
MAG<-MAG_tab[,-1]
MAG$longevity<-as.factor(MAG$longevity)
set.seed(123456)
# training set and testing set partition based 0.75 and 0.25
trainIndex <- createDataPartition(MAG$longevity, p = 0.75, list = FALSE)
train_df <- MAG[trainIndex, ]
test_df <- MAG[-trainIndex, ]
nrow(train_df);nrow(test_df)

## machine leanring prediction
## random forest
set.seed(123456)
rf_res <- randomForest(longevity~., data = train_df, ntree = 1000)
rf_res

rf_pred <- predict(rf_res, test_df,type='prob')
rf_pred <- data.frame(rf_pred)
colnames(rf_pred) <- paste(colnames(rf_pred),"_pred_RF")

## combine the true and predicted value
true_label <- dummies::dummy(test_df$longevity, sep =".")
true_label <- data.frame(true_label)
colnames(true_label) <- gsub(".*?\\.","", colnames(true_label))
colnames(true_label) <- paste(colnames(true_label),"_true")
final_df <- cbind(true_label, rf_pred)

# calculate multiROC and multiPR
roc_res <- multi_roc(final_df, force_diag=T)
unlist(roc_res$AUC)

pr_res <- multi_pr(final_df, force_diag=T)
unlist(pr_res$AUC)

## ROC curves
library(dplyr)
plot_roc_df <- plot_roc_data(roc_res) %>% as.data.frame()
plot_roc_df_g<-plot_roc_df[plot_roc_df$Group!="Macro" & plot_roc_df$Group!="Micro",] %>%
  as.data.frame()

plot_roc_df_g_centenarian <- plot_roc_df_g[1:77,]
# write.table(plot_roc_df_g_centenarian, file = "centenarian_prediction_acuracy.tsv", sep = "\t", row.names = F)
########################################################################
p<-ggplot(plot_roc_df_g_centenarian, aes(x = 1 - Specificity, y = Sensitivity)) +
  geom_path(aes(color = Group, linetype = Method), size = .5) +
  scale_color_manual(values = c("tomato", "darkgreen")) +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
               colour = 'grey', linetype = 'dashed') +
  # theme_test() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.justification = c(1, 0), legend.position = c(.95, .05),
        legend.title = element_blank(),
        legend.background = element_rect(fill = NULL, size = 0.5,
                                         linetype = "solid", colour = "black")) +
  annotate("text", x = 0.95, y = 0, label = "AUC(C) = 0.856", 
           hjust = .9, vjust = 0, size = 3, color = "black")+
  theme_test()
p
pdf("./Fig.2E.pdf", height = 10, width = 14)
p
dev.off()
```

## Fig.2F. Differential analysis of the prokaryotic consistent modulators in gut across different groups.

### (1) Differential analysis between group pairs
```{r Differential test}
library(ggClusterNet)
library(phyloseq)
library(tidyverse)
# otu<-read.table("./data_fig2/abundance_count.tsv",header=TRUE,sep="\t",row.names=1)
meta_tab<-read.table("./data_fig2/metadata_rmNA.txt",header=TRUE,sep="\t",row.names=1)
taxonomy<-read.table("./data_fig2/drep95_annotation.txt",header=TRUE,sep="\t",row.names=1)
taxonomy$Species2<-ifelse(taxonomy$Species!="s__",taxonomy$Species,rownames(taxonomy))
otutab<-read.table("./data_fig2/mag_tab.txt",sep="\t",header=TRUE,row.names=1)
MAG_large<-read_tsv("./data_fig2/MAG_Largest_comp.tsv")
MAG_tab<-otutab[MAG_large$MAG,]
taxonomy<-taxonomy[MAG_large$MAG,]
#########################################################################
# for codes annotated using "#" between 1702-1738, we only recommend runing in Rstudio mode, not under the Rmd mode, because the function "sample_data" we used here in the phyloseq Package can't work successfully when press the above Knit.
# so, here we provided the ".RData" file we provided in the following directory. Like the code in lines 1734 and 1739 to load the MAG_table and metadata of each group pair (here: E vs C)
# construct the "ps1" file
ps1 <- phyloseq(sample_data(meta_tab),
              otu_table(as.matrix(MAG_tab), taxa_are_rows=TRUE),
              tax_table(as.matrix(taxonomy))#,
              # phy_tree(tree),
              # refseq(rep)
)
# save(ps1,file="./data_fig2/ps1.RData")
# load("./data_fig2/ps1.RData")
# # pairwise comparison.
# map<- phyloseq::sample_data(ps1)
# save(map,file="./data_fig2/map.RData")
# load("./data_fig2/map.RData")
# head(map)
# id.g = map$Group %>% unique() %>% as.character() %>% combn(2)
##########################################################################
# id.g
# Differential analysis: C vs E
# i =1
#--differential analysis method：Aldex2#--------
library(ALDEx2)
# ASV_table = ps1 %>%
#   filter_taxa(function(x) sum(x ) > 0 , TRUE) %>%
#   subset_samples(Group %in% id.g[,i]) %>%
#   vegan_otu() %>% t() %>%
#   as.data.frame()
# save(ASV_table, file="./data_fig2/MAG_table_EC.RData")
load("./data_fig2/MAG_table_EC.RData")
# groupings <- ps1 %>%
#   subset_samples(Group%in% id.g[,i]) %>%
#   sample_data()
# save(groupings,file="./data_fig2/groupings_EC.RData")
load("./data_fig2/groupings_EC.RData")
groupings$ID = row.names(groupings)
results <- aldex(reads=ASV_table, conditions = groupings$Group,
                 mc.samples = 128,
                 test="t",
                 effect=TRUE,
                 include.sample.summary = FALSE,
                 verbose=T,
                 denom="all")

head(results) 
# thereafter shows the effect size of the group C vs E.
# the adjusted p-value of Weilch's t test of MAGs as the significant species between group C and E. p threshold are 0.005
tab.d1 = results %>%
  as.data.frame() %>%
  dplyr::filter(we.eBH < 0.005 & wi.eBH<0.005) %>% rownames_to_column(var = "id") %>%
  dplyr::select(id,wi.eBH) %>%
  dplyr::rename(
    OTU = id,
    p = wi.eBH
  ) %>%
  dplyr::mutate(methods = "Aldex2")

dir.create("./data_fig2/different")
write.table(results, file="./data_fig2/different/Aldex2-EC.txt", quote=FALSE, sep='\t', col.names = NA)
write.table(tab.d1, file="./data_fig2/different/Aldex2-1EC.txt", quote=FALSE, sep='\t', col.names = NA)
# #############################################################################
# id.g
# # Differential analysis: C vs Y
# i =5
library(ALDEx2)
# ASV_table = ps1 %>%
#   filter_taxa(function(x) sum(x ) > 0 , TRUE) %>%
#   subset_samples(Group %in% id.g[,i]) %>%
#   vegan_otu() %>% t() %>%
#   as.data.frame()
# save(ASV_table, file = "./data_fig2/MAG_table_CY.RData")
load("./data_fig2/MAG_table_CY.RData")
# groupings <- ps1 %>%
#   subset_samples(Group%in% id.g[,i]) %>%
#   sample_data()
# save(groupings,file="./data_fig2/groupings_CY.RData")
load("./data_fig2/groupings_CY.RData")
groupings$ID = row.names(groupings)
results <- aldex(reads=ASV_table, conditions = groupings$Group,
                 mc.samples = 128,
                 test="t",
                 effect=TRUE,
                 include.sample.summary = FALSE,
                 verbose=T,
                 denom="all")

head(results)

tab.d1 = results %>%
  as.data.frame() %>%
  dplyr::filter(we.eBH < 0.005 & wi.eBH<0.005) %>% rownames_to_column(var = "id") %>%
  dplyr::select(id,wi.eBH) %>%
  dplyr::rename(
    OTU = id,
    p = wi.eBH
  ) %>%
  dplyr::mutate(methods = "Aldex2")

dir.create("./data_fig2/different")
write.table(results, file="./data_fig2/different/Aldex2-CY.txt", quote=FALSE, sep='\t', col.names = NA)
write.table(tab.d1, file="./data_fig2/different/Aldex2-1CY.txt", quote=FALSE, sep='\t', col.names = NA)
# ###############################################################################
# id.g
# # Differential analysis: C vs L
# i =4
library(ALDEx2)
# ASV_table = ps1 %>%
#   filter_taxa(function(x) sum(x ) > 0 , TRUE) %>%
#   subset_samples(Group %in% id.g[,i]) %>%
#   vegan_otu() %>% t() %>%
#   as.data.frame()
# save(ASV_table, file = "./data_fig2/MAG_table_CL.RData")
load("./data_fig2/MAG_table_CL.RData")
# groupings <- ps1 %>%
#   subset_samples(Group%in% id.g[,i]) %>%
#   sample_data()
# save(groupings,file="./data_fig2/groupings_CL.RData")
load("./data_fig2/groupings_CL.RData")
groupings$ID = row.names(groupings)
results <- aldex(reads=ASV_table, conditions = groupings$Group,
                 mc.samples = 128,
                 test="t",
                 effect=TRUE,
                 include.sample.summary = FALSE,
                 verbose=T,
                 denom="all")

head(results) 

tab.d1 = results %>%
  as.data.frame() %>%
  dplyr::filter(we.eBH < 0.005 & wi.eBH<0.005) %>% rownames_to_column(var = "id") %>%
  dplyr::select(id,wi.eBH) %>%
  dplyr::rename(
    OTU = id,
    p = wi.eBH
  ) %>%
  dplyr::mutate(methods = "Aldex2")

dir.create("./data_fig2/different")
write.table(results, file="./data_fig2/different/Aldex2-CL.txt", quote=FALSE, sep='\t', col.names = NA)
write.table(tab.d1, file="./data_fig2/different/Aldex2-1CL.txt", quote=FALSE, sep='\t', col.names = NA)
# ###########################################################################
# id.g
# # Differential analysis: E vs Y
# i =3

library(ALDEx2)
# ASV_table = ps1 %>%
#   filter_taxa(function(x) sum(x ) > 0 , TRUE) %>%
#   subset_samples(Group %in% id.g[,i]) %>%
#   vegan_otu() %>% t() %>%
#   as.data.frame()
# save(ASV_table, file="./data_fig2/MAG_table_EY.RData")
load("./data_fig2/MAG_table_EY.RData")
# groupings <- ps1 %>%
# subset_samples(Group%in% id.g[,i]) %>%
# sample_data()
# save(groupings,file="./data_fig2/groupings_EY.RData")
load("./data_fig2/groupings_EY.RData")
groupings$ID = row.names(groupings)

results <- aldex(reads=ASV_table, conditions = groupings$Group,
                 mc.samples = 128,
                 test="t",
                 effect=TRUE,
                 include.sample.summary = FALSE,
                 verbose=T,
                 denom="all")

head(results) 

tab.d1 = results %>%
  as.data.frame() %>%
  dplyr::filter(we.eBH < 0.005 & wi.eBH<0.005) %>% rownames_to_column(var = "id") %>%
  dplyr::select(id,wi.eBH) %>%
  dplyr::rename(
    OTU = id,
    p = wi.eBH
  ) %>%
  dplyr::mutate(methods = "Aldex2")

dir.create("./data_fig2/different")
write.table(results, file="./data_fig2/different/Aldex2-EY.txt", quote=FALSE, sep='\t', col.names = NA)
write.table(tab.d1, file="./data_fig2/different/Aldex2-1EY.txt", quote=FALSE, sep='\t', col.names = NA)
# #######################################################################################
# ALDEx2分析的CE/CY组差异菌中共有菌
CY_DIF<-read.table("./data_fig2/different/Aldex2-1CY.txt",header=T,row.names=1,sep="\t")
EC_DIF<-read.table("./data_fig2/different/Aldex2-1EC.txt",header=T,row.names=1,sep="\t")
CL_DIF<-read.table("./data_fig2/different/Aldex2-1CL.txt",header=T,row.names=1,sep="\t")
DIFinC<-intersect(CY_DIF$OTU,EC_DIF$OTU) %>% intersect(CL_DIF$OTU)
length(DIFinC)

# 读入差异分析表
EC_DIF_TAB<-read.table("./data_fig2/different/Aldex2-EC.txt",header=T,row.names=1,sep="\t")
CY_DIF_TAB<-read.table("./data_fig2/different/Aldex2-CY.txt",header=T,row.names=1,sep="\t")
EY_DIF_TAB<-read.table("./data_fig2/different/Aldex2-EY.txt",header=T,row.names=1,sep="\t")
CL_DIF_TAB<-read.table("./data_fig2/different/Aldex2-CL.txt",header=T,row.names=1,sep="\t")
# 选出共有差异菌EC
EC_DIF_TAB_COMM<-EC_DIF_TAB[DIFinC,c(2,3,6,11)] 
EC_DIF_TAB_COMM<-EC_DIF_TAB_COMM %>% sort_by(EC_DIF_TAB_COMM$effect,decreasing=TRUE)
# 选择效应值正值top15和负值top15的物种展示
EC_DIF_TAB_COMM<-EC_DIF_TAB_COMM[c(1:35),]
dim(EC_DIF_TAB_COMM)
names(EC_DIF_TAB_COMM)
colnames(EC_DIF_TAB_COMM)[4]<-"p_value"
names(EC_DIF_TAB_COMM)
#####################################################
# CY
CY_DIF_TAB_COMM<-CY_DIF_TAB[DIFinC,c(2,3,6,11)]
CY_DIF_TAB_COMM<-CY_DIF_TAB_COMM[rownames(EC_DIF_TAB_COMM),]
colnames(CY_DIF_TAB_COMM)[4]<-"p_value"
names(CY_DIF_TAB_COMM)
dim(CY_DIF_TAB_COMM)
###########################################################
# EY
EY_DIF_TAB_COMM<-EY_DIF_TAB[DIFinC,c(2,3,6,11)]
EY_DIF_TAB_COMM<-EY_DIF_TAB_COMM[rownames(EC_DIF_TAB_COMM),]
colnames(EY_DIF_TAB_COMM)[4]<-"p_value"
############################################################
# CL
CL_DIF_TAB_COMM<-CL_DIF_TAB[DIFinC,c(2,3,6,11)]
CL_DIF_TAB_COMM<-CL_DIF_TAB_COMM[rownames(EC_DIF_TAB_COMM),]
colnames(CL_DIF_TAB_COMM)[4]<-"p_value"
################################################################################
# 校对比较关系
##################
# C vs L
CL_DIF_TAB_COMM$Group<-"CvsL"
CL_DIF_TAB_COMM$Effect<- -CL_DIF_TAB_COMM$effect
CL_DIF_TAB_COMM<-CL_DIF_TAB_COMM[,c(5,6,4)]
##################
# C vs E
EC_DIF_TAB_COMM$Group<-"CvsE"
EC_DIF_TAB_COMM$Effect<- -EC_DIF_TAB_COMM$effect
EC_DIF_TAB_COMM<-EC_DIF_TAB_COMM[,c(5,6,4)]
################
# C vs Y
CY_DIF_TAB_COMM$Group<-"CvsY"
CY_DIF_TAB_COMM$Effect<- -CY_DIF_TAB_COMM$effect
CY_DIF_TAB_COMM<-CY_DIF_TAB_COMM[,c(5,6,4)]
################
# E vs Y
EY_DIF_TAB_COMM$Group<-"EvsY"
EY_DIF_TAB_COMM$Effect<- -EY_DIF_TAB_COMM$effect
EY_DIF_TAB_COMM<-EY_DIF_TAB_COMM[,c(5,6,4)]
##################################################
EC_DIF_TAB_COMM$MAG<-rownames(EC_DIF_TAB_COMM)
CL_DIF_TAB_COMM$MAG<-rownames(CL_DIF_TAB_COMM)
CY_DIF_TAB_COMM$MAG<-rownames(CY_DIF_TAB_COMM)
EY_DIF_TAB_COMM$MAG<-rownames(EY_DIF_TAB_COMM)
###给行名编号
rownames(EC_DIF_TAB_COMM)<-1:35
rownames(CL_DIF_TAB_COMM)<-36:70
rownames(CY_DIF_TAB_COMM)<-71:105
rownames(EY_DIF_TAB_COMM)<-106:140
###合并为一个表
difference_species<-rbind(EC_DIF_TAB_COMM,CL_DIF_TAB_COMM,CY_DIF_TAB_COMM,EY_DIF_TAB_COMM)
df_tab<-difference_species[,c(4,1,2,3)]
write.table(df_tab, file="./data_fig2/different/difference_species2.txt", quote=FALSE, sep='\t', col.names = NA)
```

### (2) Calculating prevalence of species
```{r Calculating prevalence}
library(ggplot2)
library(patchwork)
library(dplyr)
library(reshape2)
library(ggprism)
library(plyr)
library(magrittr)
library(ggfun)
library(cowplot)
################################################################
# calculating prevalence
# Load data
data_prokaryotes <- read.table("./data_fig2/mag_tab.txt", sep = "\t", header = TRUE, row.names=1,check.names = FALSE)
design_C <- read.table("./data_fig2/different/design_C.txt", sep = "\t", header = TRUE, row.names = 1)
design_C<- design_C %>% dplyr::select(Group)
design_C$sample_new<-rownames(design_C)
dim(design_C)
design_L <- read.table("./data_fig2/different/design_L.txt", sep = "\t", header = TRUE, row.names = 1) %>% dplyr::select("Group")
design_L$sample_new<-rownames(design_L)
dim(design_L)
design_E <- read.table("./data_fig2/different/design_E.txt", sep = "\t", header = TRUE, row.names = 1) %>% dplyr::select("Group")
design_E$sample_new<-rownames(design_E)
dim(design_E)
design_Y <- read.table("./data_fig2/different/design_Y.txt", sep = "\t", header = TRUE, row.names = 1) %>% dplyr::select("Group")
design_Y$sample_new<-rownames(design_Y)
dim(design_Y)
#########################
difference_species<-read.table("./data_fig2/different/difference_species.csv",header=T,sep=",",row.names=1)
# View(difference_species)
rownames(difference_species)<-difference_species$ID
dim(difference_species)

data_prokaryotes01 <- data_prokaryotes %>% apply(2, function(x) x / sum(x))
data_prokaryotes02 <- as.data.frame(t(data_prokaryotes01))

# Function to process each design group
process_design <- function(design, data_prokaryotes02, all_counts_value) {
  data_prokaryotes_group <- data_prokaryotes02[rownames(data_prokaryotes02) %in% rownames(design), ] %>% t() %>% as.data.frame()
  
  zero_counts <- rowSums(data_prokaryotes_group == 0)
  data_species2 <- data_prokaryotes_group %>%
    mutate(zero_counts = zero_counts,
           sample_percent = round(1 - zero_counts / all_counts_value, 6))
  
  data_species3 <- data_species2[rownames(data_species2) %in% rownames(difference_species), ]
  return(data_species3)
}
##############################################################
# Process each design group and write to CSV
# C
data_species3_C <- process_design(design_C, data_prokaryotes02, 108)
# View(data_species3_C)
write.csv(data_species3_C, "./data_fig2/different/prevalence_C.csv")
###############################################################
# L
data_species3_L <- process_design(design_L, data_prokaryotes02, 61)
# View(data_species3_L)
write.csv(data_species3_L, "./data_fig2/different/prevalence_L.csv")
#################################################################
# E
data_species3_E <- process_design(design_E, data_prokaryotes02, 72)
# View(data_species3_E)
write.csv(data_species3_E, "./data_fig2/different/prevalence_E.csv")
#################################################################
# Y
data_species3_Y <- process_design(design_Y, data_prokaryotes02, 65)
# View(data_species3_Y)
write.csv(data_species3_Y, "./data_fig2/different/prevalence_Y.csv")
```
### (3) Calculating relative abundance of species
```{r Calculating relative abundance}
library(dplyr)
##################
data_rare <- read.table("./data_fig2/mag_tab.txt", sep = "\t", header = TRUE, check.names = FALSE,row.names=1)
# View(data_rare)
colSums(data_rare)[1:10]
rel_tab<-data_rare %>% (function(x) x/colSums(x))
# View(rel_tab)
colSums(rel_tab)[1:10]
###############
Meta<-read.table("./data_fig2/metadata_rmNA.txt",sep="\t",header=T,check.names=FALSE)
# View(Meta)
Meta_C<-Meta[Meta$Group=="C",]
dim(Meta_C)
Meta_L<-Meta[Meta$Group=="L",]
dim(Meta_L)
Meta_E<-Meta[Meta$Group=="E",]
dim(Meta_E)
Meta_Y<-Meta[Meta$Group=="Y",]
dim(Meta_Y)
################## select MAG_table of each group
rel_tab_C<-rel_tab[,c(Meta_C$SampleID)]
rel_tab_L<-rel_tab[,c(Meta_L$SampleID)]
rel_tab_E<-rel_tab[,c(Meta_E$SampleID)]
rel_tab_Y<-rel_tab[,c(Meta_Y$SampleID)]
################### generate the means column
rel_tab_C$species_C_mean<-rowMeans(rel_tab_C)
rel_tab_L$species_L_mean<-rowMeans(rel_tab_L)
rel_tab_E$species_E_mean<-rowMeans(rel_tab_E)
rel_tab_Y$species_Y_mean<-rowMeans(rel_tab_Y)
##### combine the original table with the new columns.
otutab<-cbind(rel_tab,rel_tab_C$species_C_mean,rel_tab_L$species_L_mean,
              rel_tab_E$species_E_mean,rel_tab_Y$species_Y_mean)
dim(otutab)
colnames(otutab)[307:310]<-c("species_C_mean","species_L_mean",
                             "species_E_mean","species_Y_mean")
################################################################
# selection the differential species (MAGs)
otutab_mean<-otutab[,307:310]
# View(otutab_mean)
##################
library(tidyr)
differ_species<-read.table("./data_fig2/different/difference_species.csv",sep=",",row.names=1,header=T)
# View(differ_species)
otutab_mean_final<-otutab_mean[c(differ_species$ID),]
dim(otutab_mean_final)
otutab_mean_final$MAG<-rownames(otutab_mean_final)
prevalence2<-otutab_mean_final %>%
  pivot_longer(cols=c(species_C_mean,species_L_mean,
                      species_E_mean,species_Y_mean),
               names_to="Group",values_to="RA")
prevalence2<-prevalence2 %>% sort_by(prevalence2$Group)
prevalence2$Group<-c(rep("Centenarian",35),rep("Elderly",35),
                     rep("Offspring",35),rep("Young",35))
#########################################################################
write.table(prevalence2, file="./data_fig2/different/prevalence2.txt", 
            quote=FALSE, sep='\t', col.names = NA)

```
### (4) Heatmapbarplot of the differential species
```{r heatmapbarplot}
library(ggplot2)
library(patchwork)
library(dplyr)
library(reshape2)
library(ggprism)
library(plyr)
library(magrittr)
library(ggfun)
library(cowplot)
##########################################################################
# 
# Load data
data1 <- read.table("./data_fig2/difference_species2.txt",header = TRUE,row.names = 1,sep = "\t")
data1[which(data1$p_value<0.01),'sig'] <- '*'
data1[which(data1$p_value<0.001),"sig"]<-"**"
data1[which(data1$p_value<0.0001),"sig"]<-"***"

# load the ordered differential species (order by effect size of each species)
level<-read.csv("./data_fig2/levels.csv",header=TRUE,sep=",")
list=level$levels
list
# Set order
data1$Species2 = factor(data1$MAG, levels = rev(list))
data1 = data1 %>%
  mutate(Species2 = ordered(Species2,
                            levels=list
  ))
data1$Group<-factor(data1$Group,levels=c("CvsY","CvsL","CvsE","EvsY"))
# plot
# data selection
# data <- data1[(data1$Difference)< -2 | (data1$Difference) > 0.1,]
# dim(data)
data<-data1
# write.table(data,file="data_differential_test.tsv", sep = "\t", row.names = F)
# Plot
p1 <- ggplot(data, aes(Group,Species2)) +  
  geom_tile(aes(fill=Effect), color="white") +    
  geom_text(aes(label=sig), color="black", size=5,vjust = 0.9) + 
  scale_fill_gradient2(low='darkgreen', high='red',mid = 'white',name=paste0("Effect.")) +
  labs(x=NULL,y=NULL) +  
  theme_classic()+
  theme(axis.text.x = element_text(size=10,angle = 45,hjust = 1,color = "black"),            
        axis.text.y = element_text(size=10,color = "black"), 
        axis.line.x = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.length = unit(2.0, "mm"),
        panel.background=element_blank(),
        legend.position = "left")
p1
ggsave(paste("./data_fig2/different/age_prokaryotes",".pdf", sep=""), p1, width=89 * 2, height=180 *1.5, unit='mm')

# Bar plot relative abundance
# 
imp_species <- read.table("./data_fig2/prevalence2.txt", row.names=1,header = TRUE, sep = "\t")
imp_species <- imp_species %>%
  mutate(Species2 = ordered(MAG,
                            levels=list))
imp_species$RA<-100*imp_species$RA
# obtain the unique group names
# groups <- unique(imp_species$Group)
groups <- c("Centenarian", "Offspring","Elderly","Young")
# assign names of each group
colors <- c("Centenarian" = "tomato", "Offspring"="orange",
            "Elderly" = "steelblue",  "Young" = "darkgreen")
# write.table(imp_species, file="imp_speices.tsv", sep = "\t", row.names = F)
plots <- lapply(seq_along(groups), function(i) {
  g <- groups[i]
  p <- ggplot(subset(imp_species, Group == g), aes(x = Species2, y = RA)) +
    geom_bar(stat = "identity", fill = colors[g]) +
    coord_flip() +
    theme_classic() +
    theme(text = element_text(family = 'sans', size = 14),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = "none",
          axis.line.x = element_blank(),
          axis.line.y = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_text(size = 10, angle = 45, hjust = 1, color = "black"),
          axis.text.y = element_blank()
    ) +
    geom_hline(yintercept = c(0,2,4,6), colour = 'black', lwd = 0.36, linetype = "dashed") +
    #scale_y_continuous(expand = expansion(0, 0), limits = c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1)) +
    #labs(title = paste("Prevalence for", g))
    facet_set(label=paste(g))
  
  if (i != 1) {
    p <- p + theme(axis.text.y = element_blank(),
                   axis.ticks.y = element_blank())
  }
  
  return(p)
})

final_plot2 <- plot_grid(plotlist = plots, ncol = 4, byrow=TRUE, rel_widths = c(1, 1, 1, 1))

#print(final_plot)

library(cowplot)
p3 <- ggdraw() +
  draw_plot(p1, 0, 0.01, .35, 0.945)+
  draw_plot(final_plot2, 0.350, 0.0105, .58, 0.97)
p3
pdf("./Fig.2F.pdf", height = 10, width = 14)
p3
dev.off()
```
```{r}
sessionInfo()
```


