---
title: "Fig3"
author: "Zhihao Zhu(朱志豪), Yong-Xin Liu(刘永鑫 )"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    theme: cerulean
    highlight: haddock
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: yes
    code_fold: show
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(collapse = T,  comment="#>", echo=T, message=F, warning=F)
```

## Fig.3a. Diagram of CGBB constructio
This figure is manually drawn by Biorender (https://app.biorender.com) 

```{r Fig.3a}
# load Fig.3a
knitr::include_graphics("./Figures/Fig.3a.pdf")
```

## Fig.3b. Phylogenetic tree of 16S rDNA
16S analysis process follows the EasyAmplicon pipeline (https://doi.org/10.1002/imt2.83), Tree editing using online websites iTOL (https://itol.embl.de)

```{r Fig.3b}
# load Fig.3b
knitr::include_graphics("./Figures/Fig.3b.pdf")
```

## Fig.3c. Phylogenetic tree of 1557 genomes
Genome analysis process follows the EasyMetagenome pipeline (https://doi.org/10.1002/imt2.83) and EasyGenome (unpublished), Tree editing using online websites iTOL (https://itol.embl.de)

```{r Fig.3c}
# load Fig.3c
knitr::include_graphics("./Figures/Fig.3c.pdf")
```

## Fig.3d. Species Venn diagram of CGBB, CGR2 and HGG
This figure is manually drawn by Evenn (https://www.bic.ac.cn/test/venn/#/)

```{r Fig.3d}
# load Fig.3d
knitr::include_graphics("./Figures/Fig.3d.pdf")
```

## Fig.3e. Venn diagram depicting overlapping metagenomes and genomes
This figure is manually drawn by Evenn (https://www.bic.ac.cn/test/venn/#/)

```{r Fig.3e}
# load Fig.3e
knitr::include_graphics("./Figures/Fig.3e.pdf")
```

## Fig.3f. Relative abundance of A. ihumii
The relative abundance of A. ihumii across different age groups. Wilcox rank sum test.

```{r Fig.3f}
library(ggplot2)
library(tidyverse)
library(agricolae)
library(car)
library(reshape2)
library(ggpubr)
library(rstatix)
library(readxl)

############################
df <- read_excel("./Data/f_Alistipes ihumii.xlsx")
names(df) <- c("SamplesID",
               "Alistipes_ihumii_count",
               "Rarefied_samples_total_counts",
               "Relative_abundance_of_Alistipes_ihumii",
               "Group")
df$Group <- factor(df$Group,
                   levels = c("Centenarian","Offspring","Elderly","Young"))

############################
tapply(df$Relative_abundance_of_Alistipes_ihumii,
       df$Group,
       shapiro.test)
bartlett.test(Relative_abundance_of_Alistipes_ihumii ~ Group, data = df)

############################
variance <- with(df,
                 kruskal(Relative_abundance_of_Alistipes_ihumii,
                         Group,
                         group = TRUE,
                         p.adj = "bon"))
mark <- as.data.frame(variance$groups)
mark$Group <- rownames(mark)
############################
stat.test <- df %>%
  wilcox_test(Relative_abundance_of_Alistipes_ihumii ~ Group,
              p.adjust.method = "bonferroni") %>%
  add_significance()
stat.test <- stat.test %>%
  add_xy_position(x = "Group")

############################
df$log_abundance <- log10(df$Relative_abundance_of_Alistipes_ihumii + 1e-6)
mark$y_offset <- max(df$log_abundance) * 1.05

############################
p1 <- ggplot(df,
             aes(x = Group,
                 y = log_abundance,
                 fill = Group)) +
  geom_boxplot(width = 0.55,
               outlier.shape = NA,
               alpha = 0.8,
               color = "black") +
  geom_jitter(aes(color = Group),
              width = 0.18,
              size = 2,
              alpha = 0.6,
              show.legend = FALSE) +
  scale_fill_manual(values = c("tomato",
                               "orange",
                               "steelblue",
                               "darkgreen")) +
  scale_color_manual(values = c("tomato",
                                "orange",
                                "steelblue",
                                "darkgreen")) +
  geom_text(data = mark,
            aes(x = Group,
                y = y_offset,
                label = groups),
            inherit.aes = FALSE,
            size = 6,
            fontface = "bold") +
  xlab("") +
  ylab(expression(log[10]*"(Relative abundance + 1e-6)")) +
  theme_classic(base_size = 15) +
  theme(
    axis.text = element_text(size = 13),
    axis.title.y = element_text(size = 15, face = "bold"),
    legend.position = "none"
  )
ggsave("Fig.3f.pdf", p1, width = 183, height = 119, units = "mm")
```

```{r}
# load Fig.3f
knitr::include_graphics("./Figures/Fig.3f.pdf")
```


## Fig.3g. Comparative analysis of orthologous gene families
This figure is manually drawn by Evenn (https://www.bic.ac.cn/test/venn/#/)

```{r Fig.3g}
# load Fig.3g
knitr::include_graphics("./Figures/Fig.3g.pdf")
```

## Fig.3h. Whole-genome collinearity analysis of the A. ihumii strains
This figure revealed the genomic heterogeneity between SX_C120 and SX_G294 (data of NGS), Results ganerated by Orthofinder

```{r Fig.3h}
# load Fig.3h
knitr::include_graphics("./Figures/Fig.3h.pdf")
```
